---
title: '[0] General Summary: QI gPPS Analysis Report'
author: "CNPI AMR"
date: "Last compiled on `r format(Sys.time(), '%A %d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    theme: flatly
    df_print: paged
    highlight: tango
    fig_width: 10
    fig_height: 6
    fig_caption: true
    code_folding: hide
  pdf_document:
    toc: true
    toc_depth: '3'
---


<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
  📊 Report Overview
</h1>

This report presents a **summary analysis** of the Global PPS (gPPS) inpatient dataset using the **WHO AWaRe classification framework**.  
The focus is on **empirical antibiotic prescribing practices** in adults with **Seven different** **community-acquired infections (CAIs)** in addition to **surgical prophylaxis (SP)**, aligned with WHO's AWaRe Quality Indicators (QIs).

<div style="background-color: #e9f7fa; border-left: 6px solid #17a2b8; padding: 12px; margin-top: 20px; margin-bottom: 20px;">
<strong>1- Clinical Sepsis of Unknown Origin</strong> (Based on WHO AWaRe book)<br>
▸ <strong>gPPS diagnostic code:</strong> <code>SEPSIS</code><br>
▸ <strong>gPPS definition:</strong> Sepsis of any origin (e.g., urosepsis, pulmonary sepsis, etc.), sepsis syndrome, or septic shock with no clear anatomic site, including candidemia with septic symptoms.
</div>

<div style="background-color: #e9f7fa; border-left: 6px solid #17a2b8; padding: 12px; margin-top: 20px; margin-bottom: 20px;">
<strong>2- Bacterial Meningitis</strong> (Based on WHO AWaRe book)<br>
▸ <strong>gPPS diagnostic code:</strong> <code>CNS</code><br>
▸ <strong>gPPS definition:</strong> Includes central nervous system infections.
</div>

<div style="background-color: #e9f7fa; border-left: 6px solid #17a2b8; padding: 12px; margin-top: 20px; margin-bottom: 20px;">
<strong>3- Community-acquired Pneumonia</strong> (Based on WHO AWaRe book)<br>
▸ <strong>gPPS diagnostic code:</strong> <code>Pneu</code><br>
▸ <strong>gPPS definition:</strong> Includes pneumonia and other lower respiratory tract infections (LRTIs).
</div>

<div style="background-color: #e9f7fa; border-left: 6px solid #17a2b8; padding: 12px; margin-top: 20px; margin-bottom: 20px;">
<strong>4- Intra-abdominal Infections</strong> (Based on WHO AWaRe book)<br>
▸ <strong>gPPS diagnostic code:</strong> <code>IA</code><br>
▸ <strong>gPPS definition:</strong> Includes hepatobiliary infections, intra-abdominal abscesses, and general abdominal sepsis.
</div>

<div style="background-color: #e9f7fa; border-left: 6px solid #17a2b8; padding: 12px; margin-top: 20px; margin-bottom: 20px;">
<strong>5- Upper Urinary Tract Infections</strong> (Based on WHO AWaRe book)<br>
▸ <strong>gPPS diagnostic code:</strong> <code>Pye</code><br>
▸ <strong>gPPS definition:</strong> Includes pyelonephritis and catheter-associated upper urinary tract infections.
</div>

<div style="background-color: #e9f7fa; border-left: 6px solid #17a2b8; padding: 12px; margin-top: 20px; margin-bottom: 20px;">
<strong>6- Skin/Soft Tissue Infections</strong> (Based on WHO AWaRe book)<br>
▸ <strong>gPPS diagnostic code:</strong> <code>SST</code><br>
▸ <strong>gPPS definition:</strong> Includes cellulitis, wound infections (including surgical site infections), deep soft tissue not involving bone (e.g., infected pressure ulcers, diabetic ulcers), and abscesses.
</div>

<div style="background-color: #e9f7fa; border-left: 6px solid #17a2b8; padding: 12px; margin-top: 20px; margin-bottom: 20px;">
<strong>7- Bone and Joint Infections</strong> (Based on WHO AWaRe book)<br>
▸ <strong>gPPS diagnostic code:</strong> <code>BJ</code><br>
▸ <strong>gPPS definition:</strong> Includes septic arthritis (including prosthetic joint infections) and osteomyelitis.
</div>

<div style="background-color: #e9f7fa; border-left: 6px solid #17a2b8; padding: 12px; margin-top: 20px; margin-bottom: 20px;">
<strong>8- Surgical Prophylaxis</strong> (Based on WHO AWaRe book)<br>
▸ <strong>gPPS diagnostic code:</strong> <code>Proph</code> (including all surgical prophylaxis codes)<br>
▸ <strong>gPPS indication:</strong> <code>SP1, SP2, SP3</code><br>
▸ <strong>gPPS definition:</strong> Antibiotics given before, during, or after surgical procedures.
</div>

---

<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
💬 Additional Notes
</h2>

- Each condition was mapped based on **clinical assumptions** that align WHO QIs with gPPS diagnostic coding.
- The **intravenous (IV) route** was identified using the gPPS \"Route\" code <code>P</code> (Parenteral), encompassing IV, intrathecal, and intraperitoneal administration.
  - While \"P\" is not exclusively IV, it is used here as a **proxy for IV administration** given its predominance in empirical treatment practices.
- This script, along with subsequent ones, implements the WHO AWaRe (Access, Watch, Reserve) antibiotic use QIs for managing the conditions mentioned above in **adult inpatients** with CAIs or SP.
- It uses standardised  data from the gPPS, specifically extracted from the **Excel-based outputs** received from gPPS by participating hospitals.


---
<div style="background-color: #e9f7fa; border-left: 6px solid #17a2b8; padding: 12px; margin-top: 10px;">
Only <strong>adult patients</strong> on <strong>empirical treatment</strong> with <strong>CAIs</strong> or <strong>SP</strong> indications deemed eligible for this analysis.
</div>

***

<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
🔎 Patients eligibility check
</h2>


```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}
rm(list = ls()) #clear global environment

# Define required packages
packages <- c(
  "dplyr", 
  "tidyverse", 
  "readxl", 
  "glue", 
  "purrr",
  "tidyr",
  "scales",
  "htmltools", 
  "ggtext", 
  "forcats",
  "kableExtra"
)

# Install missing packages
new_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
if (length(new_packages)) install.packages(new_packages)

# Load all packages
invisible(lapply(packages, library, character.only = TRUE))



# Read the sheets (Patient & Department forms)

data_deps <- read_excel("HA-Global-PPS_example_dummy data.xlsx", sheet = "Department forms")
data_patients_all <- read_excel("HA-Global-PPS_example_dummy data.xlsx", sheet = "Patient forms")

# Select the needed data and merge the sheets to create a simpler version.
data_patients <- data_patients_all %>%
  select("Survey Number", "Department name", "Department type", "Age years", "AWaRe", "Diagnosis code", "Indication", "Treatment")

# Standardised Proph codes to make it easier in coding
data_patients <- data_patients %>%
  mutate(
    `Diagnosis code` = ifelse(
      Indication %in% c("SP1", "SP2", "SP3"),
      "Proph",
      `Diagnosis code`
    )
  )


data_patients <- data_patients %>%
  mutate(
    AWaRe = ifelse(
      toupper(AWaRe) == "NOT_RECOMMENDED",
      "NOT RECOMMENDED",
      AWaRe
    )
  )

# Define the specific infection types to include
infection_types <- c("SEPSIS", "CNS", "Pneu", "IA", "Pye", "SST", "BJ", "Proph")

AWaRe_abx <- c("ACCESS", "WATCH", "RESERVE", "NOT RECOMMENDED", "UNCLASSIFIED")

data_patients[data_patients==""]<-NA     # makes all empty spaces to N/A



# Define diagnostic codes and their labels
diagnostic_labels <- c(
  SEPSIS = "Undifferentiated Sepsis",
  CNS    = "Meningitis",
  Pneu   = "Respiratory Tract Infection",
  IA     = "Intra-abdominal Infection",
  Pye    = "Upper Urinary Tract Infection",
  SST    = "Skin/Soft Tissue Infection",
  BJ     = "Bone/Joint Infection",
  Proph  = "Surgical Prophylaxis"
)

# Indications for surgical prophylaxis
surgical_indications <- c("SP1", "SP2", "SP3")

# Count eligible cases (adult patients on empiric antibiotics for CAIs/ or SP)
eligible_counts <- data_patients %>%
  filter(`Diagnosis code` %in% names(diagnostic_labels)) %>%
  mutate(
    AWaRe_compatible = case_when(
      `Diagnosis code` == "Proph" & Indication %in% surgical_indications & `Age years` >= 18 & Treatment == "EMPIRICAL" ~ TRUE,
      `Diagnosis code` != "Proph" & Indication == "CAI" & `Age years` >= 18 & Treatment == "EMPIRICAL" ~ TRUE,
      TRUE ~ FALSE
    )
  ) %>%
  filter(AWaRe_compatible) %>%
  filter(AWaRe %in% AWaRe_abx) %>%
  distinct(`Diagnosis code`, `Survey Number`) %>%
  count(`Diagnosis code`)

# Merge with full diagnostics
full_diagnostics <- tibble(`Diagnosis code` = names(diagnostic_labels))

# Prepare cleaned data
eligible_summary <- full_diagnostics %>%
  left_join(eligible_counts, by = "Diagnosis code") %>%
  mutate(
    `N of Eligible Patients` = replace_na(n, 0),
    Condition = diagnostic_labels[`Diagnosis code`],
    `Analysis suitability` = case_when(
      `N of Eligible Patients` > 10 ~ "✅",
      `N of Eligible Patients` == 0 ~ "⚠️",
      TRUE ~ "⚠️"
    )
  ) %>%
  arrange(`Diagnosis code`) %>%
  select(Condition, `N of Eligible Patients`, `Analysis suitability`)

# Build HTML table header inside a centered div
table_html <- glue("
<div style='text-align: center;'>
<table class='table table-striped table-hover' style='margin: auto; font-size: 14px;'>
  <thead style='background-color: #f8f9fa;'>
    <tr>
      <th style='text-align:left;'>Condition</th>
      <th style='text-align:center;'>N of Eligible Patients</th>
      <th style='text-align:center;'>Analysis Suitability</th>
    </tr>
  </thead>
  <tbody>
")

# Add rows dynamically
for (i in seq_len(nrow(eligible_summary))) {
  table_html <- glue("{table_html}
    <tr>
      <td style='text-align:left;'>{eligible_summary$Condition[i]}</td>
      <td style='text-align:center;'>{eligible_summary$`N of Eligible Patients`[i]}</td>
      <td style='text-align:center;'>{eligible_summary$`Analysis suitability`[i]}</td>
    </tr>")
}

# Close table and div
table_html <- glue("{table_html}
  </tbody>
</table>
</div>
")

# Display it
HTML(table_html)


```



<br><div style='background-color: #f8f9fa; padding: 10px; border-left: 5px solid #17a2b8;'>
  <strong>💡 Note:</strong> The script is designed to work best with <strong>>10</strong> eligible cases per diagnostic group. Groups with fewer patients will still run, but results may be limited in insights and interpretability. <br>
</div>

<div style="background-color: #f8f9fa; border-left: 5px solid #ffc107; padding: 10px; margin-top: 10px;">
<strong>💡 Important:</strong> Groups with fewer than 10 patients are analysed with caution for interpretability.
</div>


***


<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
🏥 Admissions & Treatments by Department </h1>

This section summrises the number of admitted and treated patients in different department across the hospital 
```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}
# summarise total patients in the hospital
total_patients_text <- sprintf(
  "The total number of patients admitted in the hospital is <strong>%d</strong>.", 
  sum(data_deps$Patients, na.rm = TRUE)
)

# Patients per Department Type summary
patients_per_department_text <- data_deps %>%
  group_by(`Department type`) %>%
  summarise(Patients = sum(Patients, na.rm = TRUE), .groups = "drop") %>%
  mutate(
    Summary = sprintf("Department type: <strong>%s</strong> has <strong>%d</strong> patients.", `Department type`, Patients)
  ) %>%
  pull(Summary) %>%
  paste(collapse = "\n")

# Patients per Activity Code summary (ICU, Medical, Surgical)
patients_per_activity_text <- data_deps %>%
  group_by(`Activity code`) %>%
  summarise(Patients = sum(Patients, na.rm = TRUE), .groups = "drop") %>%
  mutate(
    Summary = sprintf("Activity Code: <strong>%s (%s)</strong> has <strong>%d</strong> patients.", `Activity code`,
                      case_when(
                        `Activity code` == "IC" ~ "ICU",
                        `Activity code` == "S" ~ "Surgical",
                        `Activity code` == "M" ~ "Medical",
                        TRUE ~ "Unknown"
                      ), Patients)
  ) %>%
  pull(Summary) %>%
  paste(collapse = "\n")

# summarise total treated patients in the hospital
total_treated_text <- sprintf(
  "The total number of treated patients in the hospital is <strong>%d</strong>.", 
  sum(data_deps$`Treated patients`, na.rm = TRUE)
)

# Treated patients per Department Type summary
treated_per_department_text <- data_deps %>%
  group_by(`Department type`) %>%
  summarise(Treated_Patients = sum(`Treated patients`, na.rm = TRUE), .groups = "drop") %>%
  mutate(
    Summary = sprintf("Department Type: <strong>%s</strong> has <strong>%d</strong> treated patients.", `Department type`, Treated_Patients)
  ) %>%
  pull(Summary) %>%
  paste(collapse = "\n")

# Treated patients per Activity Code summary (ICU, Medical, Surgical)
treated_per_activity_text <- data_deps %>%
  group_by(`Activity code`) %>%
  summarise(Treated_Patients = sum(`Treated patients`, na.rm = TRUE), .groups = "drop") %>%
  mutate(
    Summary = sprintf("Activity Code: <strong>%s (%s)</strong> has <strong>%d</strong> treated patients.", `Activity code`,
                      case_when(
                        `Activity code` == "I" ~ "ICU",
                        `Activity code` == "S" ~ "Surgical",
                        `Activity code` == "M" ~ "Medical",
                        TRUE ~ "Unknown"
                      ), Treated_Patients)
  ) %>%
  pull(Summary) %>%
  paste(collapse = "\n")


# Convert text blocks into HTML bullet lists
admit_dept_html <- paste0("<li>", strsplit(patients_per_department_text, "\n")[[1]], "</li>", collapse = "")
admit_activity_html <- paste0("<li>", strsplit(patients_per_activity_text, "\n")[[1]], "</li>", collapse = "")
treat_dept_html <- paste0("<li>", strsplit(treated_per_department_text, "\n")[[1]], "</li>", collapse = "")
treat_activity_html <- paste0("<li>", strsplit(treated_per_activity_text, "\n")[[1]], "</li>", collapse = "")

# Create styled HTML boxes
html_summary <- glue::glue(
  "<div style='background-color:#f8f9fa; border-left:5px solid #17a2b8; padding:15px; margin-bottom:20px; border-radius:5px;'>
    <h4 style='margin-top:0;'>🛌 <strong>Admitted Patients Summary</strong></h4>
    <p>{total_patients_text}</p>
    <strong>By Department type:</strong>
    <ul style='margin-top: 5px;'>{admit_dept_html}</ul>
    <strong>By Activity Type:</strong>
    <ul>{admit_activity_html}</ul>
  </div>

  <div style='background-color:#f8f9fa; border-left:5px solid #76a5af; padding:15px; margin-bottom:20px; border-radius:5px;'>
    <h4 style='margin-top:0;'>💉 <strong>Treated Patients Summary</strong></h4>
    <p>{total_treated_text}</p>
    <strong>By Department type:</strong>
    <ul style='margin-top: 5px;'>{treat_dept_html}</ul>
    <strong>By Activity Type:</strong>
    <ul>{treat_activity_html}</ul>
  </div>"
)

# Render output
htmltools::HTML(html_summary)

```

***

<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
💊 Overview of Antimicrobial Prescription</h1>



```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}

# Function to calculate patient metrics
calculate_patient_metrics <- function(dataset) {
  bind_rows(
    dataset %>% summarise(Metric = "Total Patients Given **Antimicrobials**", Count = n_distinct(`Survey Number`)),
    dataset %>% filter(AWaRe %in% AWaRe_abx) %>%
      summarise(Metric = "Total Patients Given **Antibiotics**", Count = n_distinct(`Survey Number`)),
    dataset %>% group_by(`Department type`) %>%
      summarise(Metric = "Patients Given **Antibiotics**", Count = n_distinct(`Survey Number`), .groups = "drop"),
    
    dataset %>% filter(grepl("Access", AWaRe, ignore.case = TRUE)) %>%
      summarise(Metric = "Patients Given **Access** Antibiotics", Count = n_distinct(`Survey Number`)),
    dataset %>% filter(grepl("Access", AWaRe, ignore.case = TRUE)) %>%
      group_by(`Department type`) %>%
      summarise(Metric = "Patients Given **Access** Antibiotics", Count = n_distinct(`Survey Number`), .groups = "drop"),
    
    dataset %>% filter(grepl("Watch", AWaRe, ignore.case = TRUE)) %>%
      summarise(Metric = "Patients Given **Watch** Antibiotics", Count = n_distinct(`Survey Number`)),
    dataset %>% filter(grepl("Watch", AWaRe, ignore.case = TRUE)) %>%
      group_by(`Department type`) %>%
      summarise(Metric = "Patients Given **Watch** Antibiotics", Count = n_distinct(`Survey Number`), .groups = "drop"),

    dataset %>% filter(grepl("Reserve", AWaRe, ignore.case = TRUE)) %>%
      summarise(Metric = "Patients Given **Reserve** Antibiotics", Count = n_distinct(`Survey Number`)),
    dataset %>% filter(grepl("Reserve", AWaRe, ignore.case = TRUE)) %>%
      group_by(`Department type`) %>%
      summarise(Metric = "Patients Given **Reserve** Antibiotics", Count = n_distinct(`Survey Number`), .groups = "drop"),

    dataset %>% filter(grepl("Not recommended", AWaRe, ignore.case = TRUE)) %>%
      summarise(Metric = "Patients Given **Not Recommended** Antibiotics", Count = n_distinct(`Survey Number`)),
    dataset %>% filter(grepl("Not recommended", AWaRe, ignore.case = TRUE)) %>%
      group_by(`Department type`) %>%
      summarise(Metric = "Patients Given **Not Recommended** Antibiotics", Count = n_distinct(`Survey Number`), .groups = "drop")
  ) %>%
    rename(Ward = `Department type`) %>%
    mutate(Ward = replace_na(Ward, "Hospital-Wide"))
}

# Function to calculate prescription metrics
calculate_prescription_metrics <- function(dataset) {
  bind_rows(
    dataset %>% summarise(Metric = "Total **Antimicrobial** Prescriptions", Count = n()),
    dataset %>% filter(AWaRe %in% AWaRe_abx) %>%
      summarise(Metric = "Total **Antibiotics** Prescriptions", Count = n()),
    dataset %>% group_by(`Department type`) %>%
      summarise(Metric = "Total **Antibiotics** Prescriptions", Count = n(), .groups = "drop"),
    
    dataset %>% filter(grepl("Access", AWaRe, ignore.case = TRUE)) %>%
      summarise(Metric = "**Access** Antibiotics", Count = n()),
    dataset %>% filter(grepl("Access", AWaRe, ignore.case = TRUE)) %>%
      group_by(`Department type`) %>%
      summarise(Metric = "**Access** Antibiotics", Count = n(), .groups = "drop"),
    
    dataset %>% filter(grepl("Watch", AWaRe, ignore.case = TRUE)) %>%
      summarise(Metric = "**Watch** Antibiotics", Count = n()),
    dataset %>% filter(grepl("Watch", AWaRe, ignore.case = TRUE)) %>%
      group_by(`Department type`) %>%
      summarise(Metric = "**Watch** Antibiotics", Count = n(), .groups = "drop"),

    dataset %>% filter(grepl("Reserve", AWaRe, ignore.case = TRUE)) %>%
      summarise(Metric = "**Reserve** Antibiotics", Count = n()),
    dataset %>% filter(grepl("Reserve", AWaRe, ignore.case = TRUE)) %>%
      group_by(`Department type`) %>%
      summarise(Metric = "**Reserve** Antibiotics", Count = n(), .groups = "drop"),

    dataset %>% filter(grepl("Not recommended", AWaRe, ignore.case = TRUE)) %>%
      summarise(Metric = "**Not Recommended** Antibiotics", Count = n()),
    dataset %>% filter(grepl("Not recommended", AWaRe, ignore.case = TRUE)) %>%
      group_by(`Department type`) %>%
      summarise(Metric = "**Not Recommended** Antibiotics", Count = n(), .groups = "drop")
  ) %>%
    rename(Ward = `Department type`) %>%
    mutate(Ward = replace_na(Ward, "Hospital-Wide"))
}

# --- ANALYSIS ---

# Filtered dataset (adults with CAI/SP diagnosis, empirical treatment)
filtered_data_patients <- data_patients %>%
  filter(
    `Diagnosis code` %in% c("SEPSIS", "CNS", "Pneu", "IA", "Pye", "SST", "BJ", "Proph"),
    Indication %in% c("CAI", "SP1", "SP2", "SP3"),
    Treatment == "EMPIRICAL",
    `Age years` >= 18
  )

# Compute metrics
summary_patients_full <- calculate_patient_metrics(data_patients)
summary_patients_filtered <- calculate_patient_metrics(filtered_data_patients)

summary_prescriptions_full <- calculate_prescription_metrics(data_patients)
summary_prescriptions_filtered <- calculate_prescription_metrics(filtered_data_patients)

# Merge full and filtered summaries
summary_patients <- full_join(summary_patients_full, summary_patients_filtered, by = c("Metric", "Ward"), suffix = c("_Full", "_Filtered")) %>%
  rename("Total patients" = Count_Full, "Patients for QIs-related groups" = Count_Filtered) %>%
  relocate(Ward, .after = Metric) %>%
  mutate(
    `Patients for QIs-related groups` = replace_na(`Patients for QIs-related groups`, 0),
    Ward = factor(Ward, levels = c("Hospital-Wide", sort(unique(Ward[Ward != "Hospital-Wide"]))))
  ) %>%
  arrange(Ward)


summary_prescriptions <- full_join(summary_prescriptions_full, summary_prescriptions_filtered, by = c("Metric", "Ward"), suffix = c("_Full", "_Filtered")) %>%
  rename("Total prescriptions" = Count_Full, "Prescriptions for QIs-related groups" = Count_Filtered) %>%
  relocate(Ward, .after = Metric) %>%
  mutate(
    `Prescriptions for QIs-related groups` = replace_na(`Prescriptions for QIs-related groups`, 0),
    Ward = factor(Ward, levels = c("Hospital-Wide", sort(unique(Ward[Ward != "Hospital-Wide"]))))
  ) %>%
  arrange(Ward)

```


***

<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📄 Patient-level Summary by Ward </h2>


```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}
summary_patients %>%
  knitr::kable(caption = "",
               format = "html") %>%
  kableExtra::kable_styling(
    full_width = FALSE,
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    font_size = 14
  )

```




***
<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📄 Prescription-level Summary by Ward </h2>

```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}
summary_prescriptions %>%
  knitr::kable(caption = "",
               format = "html") %>%
  kableExtra::kable_styling(
    full_width = FALSE,
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    font_size = 14
  )

```

<div style='background-color: #f8f9fa; padding: 10px; border-left: 5px solid #17a2b8;'>
  <strong>💡 Note:</strong> The AWaRe classification divides antibiotics into three categories: Access, Watch, and Reserve. Access antibiotics are first-line treatments with a low risk of resistance, typically recommended for common infections. Watch antibiotics are associated with a higher risk of resistance and require careful monitoring. Reserve antibiotics are reserved for critical cases involving resistant infections, typically used only when other options are ineffective </strong>.
  <br>
</div>

<div style="background-color: #f8f9fa; border-left: 6px solid #17a2b8; padding: 12px; margin-top: 20px; margin-bottom: 20px;">
  <strong>💡 Note:</strong> "Patients/Prescriptions for QI-related groups" refers specifically to patients or prescriptions involving <strong>empiric antibiotics</strong> for any of the <strong>eight pre-defined conditions</strong>.
  <br>
</div>



***

<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📈 Antibiotic Prescriptions by Diagnostic Group </h1>


This plot provides a general summary of antibiotic prescriptions across pre-defined diagnostic groups, regardless of age, indication, or type of treatment


```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=6}

# AWaRe stacking order
aware_levels_stack <- c("UNCLASSIFIED", "NOT RECOMMENDED", "RESERVE", "WATCH", "ACCESS")
aware_levels_legend <- c("ACCESS", "WATCH", "RESERVE", "NOT RECOMMENDED", "UNCLASSIFIED")


# All combinations of Diagnosis × AWaRe
all_combos <- expand_grid(
  `Diagnosis code` = names(diagnostic_labels),
  AWaRe = aware_levels_stack
)

# Summarise prescriptions
aware_summary <- data_patients %>%
  filter(`Diagnosis code` %in% names(diagnostic_labels)) %>%
  filter(!is.na(`AWaRe`), !is.na(`Diagnosis code`)) %>%
  group_by(`Diagnosis code`, AWaRe) %>%
  summarise(Prescriptions = n(), .groups = "drop") %>%
  right_join(all_combos, by = c("Diagnosis code", "AWaRe")) %>%
  mutate(Prescriptions = replace_na(Prescriptions, 0)) %>%
  group_by(`Diagnosis code`) %>%
  mutate(
    Total = sum(Prescriptions),
    Percentage = if_else(Total > 0, 100 * Prescriptions / Total, 0)
  ) %>%
  ungroup() %>%
  mutate(
    FriendlyLabel = diagnostic_labels[`Diagnosis code`],
    FriendlyLabel = factor(FriendlyLabel, levels = diagnostic_labels)
  )

# Set factor level order for fill
aware_summary$AWaRe <- factor(aware_summary$AWaRe, levels = aware_levels_stack)

# Create plot
ggplot(aware_summary, aes(x = fct_rev(FriendlyLabel), y = Percentage / 100, fill = AWaRe)) +

  geom_bar(stat = "identity", position = "fill", width = 0.85) +

  geom_text(
    aes(label = ifelse(Percentage >= 5, paste0(round(Percentage), "%"), "")),
    position = position_fill(vjust = 0.5),
    size = 3.5, color = "black"
  ) +

  geom_text(
    data = aware_summary %>%
      group_by(FriendlyLabel) %>%
      summarise(Total = max(Total), .groups = "drop"),
    aes(x = FriendlyLabel, y = 1.02, label = paste0("n=", Total)),
    inherit.aes = FALSE,
    size = 3.5,
    color = "gray30",
    hjust = 0
  ) +

  scale_fill_manual(
    breaks = aware_levels_legend,
    values = c(
      "ACCESS" = "#1b9e77",
      "WATCH" = "#ff7f00",
      "RESERVE" = "#e41a1c",
      "NOT RECOMMENDED" = "#8c510a",
      "UNCLASSIFIED" = "gray70"
    ),
    drop = FALSE
  ) +

  coord_flip(ylim = c(0, 1.04)) +

  labs(
    title = "Use of Antibiotics by Diagnosis Group (AWaRe Classification)",
    subtitle = "Percentages shown within bars; n = total prescriptions",
    x = "Diagnosis Group",
    y = "Proportion of Prescriptions",
    fill = "AWaRe Category"
  ) +

  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, size = 10, color = "gray30"),
    panel.border = element_rect(color = "gray70", fill = NA),
    legend.position = "bottom",
    legend.title = element_text(face = "bold", size = 12),
    axis.text.y = element_text(face = "bold", size = 10),
    plot.margin = margin(10, 80, 10, 10)
  ) +
  guides(fill = guide_legend(nrow = 3))


```


***

<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📈  Patient Antibiotic Prescriptions by Diagnosis & Department </h1>


This plot provides a general summary of patient-level antibiotic prescriptions for pre-defined diagnostic groups and across different departments, regardless of age, indication, or type of treatment



```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=6}

# AWaRe levels and colors
aware_levels <- c("Access", "Watch", "Reserve")
color_mapping <- c("Access" = "#238b45", "Watch" = "#FF8000", "Reserve" = "firebrick1")


# Lookup for labels
diagnostic_lookup <- tibble(
  `Diagnosis code` = names(diagnostic_labels),
  FriendlyLabel = unname(diagnostic_labels)
)

# Total patients per diagnosis (including 0s)
infection_totals <- data_patients %>%
  filter(`Diagnosis code` %in% names(diagnostic_labels)) %>%
  group_by(`Diagnosis code`) %>%
  summarise(Total_Infection_Patients = n(), .groups = "drop") %>%
  right_join(diagnostic_lookup, by = "Diagnosis code") %>%
  mutate(Total_Infection_Patients = replace_na(Total_Infection_Patients, 0))

# Step 1: Department-level data
dept_data <- data_patients %>%
  filter(`Diagnosis code` %in% names(diagnostic_labels)) %>%
  mutate(
    Antibiotic_Type = case_when(
      AWaRe == "ACCESS" ~ "Access",
      AWaRe == "WATCH" ~ "Watch",
      AWaRe == "RESERVE" ~ "Reserve",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(Antibiotic_Type)) %>%
  group_by(`Department type`, `Diagnosis code`, Antibiotic_Type) %>%
  summarise(Count = n(), .groups = "drop")

# Step 2: Add Hospital-Wide totals
hospital_data <- dept_data %>%
  group_by(`Diagnosis code`, Antibiotic_Type) %>%
  summarise(Count = sum(Count), .groups = "drop") %>%
  mutate(`Department type` = "Hospital-Wide")

# Combine ward + hospital
heatmap_data <- bind_rows(dept_data, hospital_data)

# Create all possible combinations
all_combos <- expand_grid(
  `Department type` = unique(heatmap_data$`Department type`),
  `Diagnosis code` = names(diagnostic_labels),
  Antibiotic_Type = aware_levels
)

# Merge with observed data, fill 0s
heatmap_data <- all_combos %>%
  left_join(heatmap_data, by = c("Department type", "Diagnosis code", "Antibiotic_Type")) %>%
  mutate(Count = replace_na(Count, 0))

# Add Friendly labels and totals
heatmap_data <- heatmap_data %>%
  left_join(infection_totals, by = "Diagnosis code") %>%
  mutate(
    FriendlyLabel_n = paste0(FriendlyLabel, "\n(n=", Total_Infection_Patients, ")"),
    FriendlyLabel_n = factor(
      FriendlyLabel_n,
      levels = paste0(
        unname(diagnostic_labels),
        "\n(n=", infection_totals$Total_Infection_Patients[match(names(diagnostic_labels), infection_totals$`Diagnosis code`)], ")"
      )
    ),
    Antibiotic_Type = factor(Antibiotic_Type, levels = aware_levels),
    Label = ifelse(Count > 0, as.character(Count), "")
  )

# Format department names (with Hospital-Wide styled)
heatmap_data <- heatmap_data %>%
  mutate(
    `Department type` = ifelse(`Department type` == "Hospital-Wide",
                               "<span style='color:#0072B2'><b>Hospital-Wide</b></span>",
                               `Department type`),
    `Department type` = factor(`Department type`, levels = unique(`Department type`)),
    `Department type` = fct_relevel(`Department type`, "<span style='color:#0072B2'><b>Hospital-Wide</b></span>")
  )

# Plot
ggplot(heatmap_data, aes(x = `Department type`, y = FriendlyLabel_n, fill = Antibiotic_Type)) +
  geom_tile(aes(alpha = Count), color = "white", size = 0.5) +
  geom_text(aes(label = Label), size = 3.5, fontface = "bold", color = "black") +
  facet_wrap(~Antibiotic_Type, ncol = 3) +
  scale_fill_manual(values = color_mapping) +
  scale_alpha_continuous(
    limits = c(0, max(heatmap_data$Count, na.rm = TRUE)),
    range = c(0.1, 1)
  ) +
  labs(
    title = "Distribution of Patients Receiving Antibiotics by Diagnostic Group",
    subtitle = "Access, Watch, Reserve antibiotics across hospital and wards",
    x = "Ward",
    y = "Infection Type",
    fill = "AWaRe Group"
  ) +
  theme_minimal(base_size = 12) +
theme(
    axis.text.x = ggtext::element_markdown(angle = 30, hjust = 1, size = 9),
    axis.text.y = element_text(size = 9, face = "bold"),
    strip.background = element_rect(fill = "black"),
    strip.text = element_text(color = "white", face = "bold"),
    panel.grid = element_blank(),
    legend.position = "right"
  )

```


<div style='background-color: #f8f9fa; padding: 10px; border-left: 5px solid #17a2b8;'>
  <strong>💡 Notes:</strong>
  <ul>
    <li>Counts patients prescribed at least one antimicrobial for each diagnosis.</li>
    <li>Patients may appear multiple times if they had multiple infections (same as the Global PPS standard).</li>
    <li>Patients can appear in multiple AWaRe categories if prescribed multiple types (e.g., both Access and Watch).</li>
  </ul>
</div>


***
<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📈 Treatment & Indication Patterns Across Age </h1>

This heatmap summarises the distribution across treatment types (empirical, targeted) and indications (CAI, HAI), separated by age groups.


```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=6}

# Define HAI diagnostic codes
HAI_terms <- c("HAI1", "HAI2", "HAI2-CVC-BSI", "HAI2-PVC-BSI", "HAI2-VAP", "HAI2-CAUTI",
               "HAI3", "HAI4", "HAI4-BSI", "HAI4-HAP", "HAI4-UTI", "HAI5", "HAI6")

# Define fixed categories to force presence in heatmap
expected_indications <- c("CAI", "HAI")
expected_age_groups <- c("Children", "Adult")
expected_treatments <- c("EMPIRICAL", "TARGETED")

# Prepare patient-level data
patient_level_data <- data_patients %>%
  filter(Indication %in% c("CAI", HAI_terms)) %>%
  filter(Treatment %in% c("EMPIRICAL", "TARGETED")) %>%
  filter(AWaRe %in% AWaRe_abx) %>%
  mutate(
    AgeGroup = ifelse(`Age years` < 18, "Children", "Adult"),
    Indication = ifelse(Indication %in% HAI_terms, "HAI", Indication),
    Treatment = factor(Treatment, levels = expected_treatments)
  ) %>%
  distinct(`Survey Number`, Indication, Treatment, AgeGroup)

# Create all combinations (ensures missing combinations are included as 0s)
all_combinations <- expand.grid(
  Indication = expected_indications,
  AgeGroup = expected_age_groups,
  Treatment = factor(expected_treatments, levels = expected_treatments),
  stringsAsFactors = FALSE
)

# Count patients and merge with all combinations
summary_table_QIs <- all_combinations %>%
  left_join(
    patient_level_data %>%
      group_by(Indication, AgeGroup, Treatment) %>%
      summarise(Patients = n(), .groups = "drop"),
    by = c("Indication", "AgeGroup", "Treatment")
  ) %>%
  mutate(Patients = replace_na(Patients, 0))

# Prepare data for heatmap
heatmap_data <- summary_table_QIs %>%
  pivot_wider(names_from = Treatment, values_from = Patients, values_fill = 0) %>%
  pivot_longer(cols = expected_treatments, names_to = "Treatment", values_to = "Patients") %>%
  mutate(
    Treatment = factor(Treatment, levels = expected_treatments),
    Indication = factor(Indication, levels = expected_indications),
    AgeGroup = factor(AgeGroup, levels = expected_age_groups)
  )

# Plot the heatmap
ggplot(heatmap_data, aes(x = Treatment, y = Indication, fill = Patients)) +
  geom_tile(color = "gray70", size = 0.5) +
  geom_text(aes(label = Patients), color = "black", size = 7, fontface = "bold") +
  facet_wrap(~ AgeGroup) +
  scale_fill_gradient(low = "#dceeff", high = "#004488", guide = "none") +
  labs(
    title = "Patient Distribution by Treatment, Indication and Age Group",
    x = "Treatment Type",
    y = "Indication"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.text = element_text(size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

```


<div style='background-color: #f8f9fa; padding: 10px; border-left: 5px solid #17a2b8;'>
  <strong>💡 Note:</strong> This analysis focuses on <strong>adult patients</strong> receiving <strong>empiric antibiotic therapy</strong> for <strong>CAIs</strong>.
  <br>
</div>



***

<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📈 Age-Specific Patterns in Prophylaxis Indications </h1>

This section summarises prophylaxis indications (Surgical, Medical, Other, Unknown) across adult and pediatric patients.

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=6}

# Define SP terms
SP_prophylaxis_terms <- c("SP1", "SP2", "SP3")

# Define fixed factor levels
expected_age_groups <- c("Children", "Adult")
expected_indications <- c("SP", "MP", "OTH", "UNK")

# Prepare and clean data
proph_summary_data <- data_patients %>%
  filter(Treatment == "EMPIRICAL") %>%
  filter(AWaRe %in% AWaRe_abx) %>%
  mutate(
    AgeGroup = ifelse(`Age years` < 18, "Children", "Adult"),
    Indication = case_when(
      toupper(Indication) %in% SP_prophylaxis_terms ~ "SP",
      TRUE ~ toupper(Indication)
    ),
    Indication = factor(Indication, levels = expected_indications),
    AgeGroup = factor(AgeGroup, levels = expected_age_groups)
  ) %>%
  filter(!is.na(Indication)) %>%
  distinct(`Survey Number`, Indication, AgeGroup)

# summarise and complete missing categories
proph_summary_counts <- proph_summary_data %>%
  group_by(AgeGroup, Indication) %>%
  summarise(Patients = n(), .groups = 'drop') %>%
  complete(AgeGroup = expected_age_groups,
           Indication = expected_indications,
           fill = list(Patients = 0))

# Calculate total patients per age group
group_totals <- proph_summary_counts %>%
  group_by(AgeGroup) %>%
  summarise(GroupTotal = sum(Patients), .groups = 'drop')

# Merge and calculate proportions safely
proph_prop <- proph_summary_counts %>%
  left_join(group_totals, by = "AgeGroup") %>%
  mutate(
    Proportion = ifelse(GroupTotal == 0, 0, Patients / GroupTotal),
    Indication = factor(Indication, levels = expected_indications)  # Force final level order again
  )

# Plot
ggplot(proph_prop, aes(x = AgeGroup, y = Proportion, fill = Indication)) +
  geom_bar(stat = "identity", position = "fill", width = 0.7) +
  geom_text(
    aes(label = ifelse(Patients > 0, Patients, "")),
    position = position_fill(vjust = 0.5),
    size = 5,
    fontface = "bold",
    color = "black"
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(
    values = c(
      "SP"  = "#4e79a7",  # bluish for Surgical Prophylaxis
      "MP"  = "#9ecae1",  # lighter blue for Medical Prophylaxis
      "OTH" = "#59a14f",  # green for Other
      "UNK" = "#a1d99b"   # light green for Unknown
    ),
    labels = c(
      "SP"  = "Surgical Prophylaxis",
      "MP"  = "Medical Prophylaxis",
      "OTH" = "Other Prophylaxis",
      "UNK" = "Unknown Indication"
    ),
    drop = FALSE
  ) +
  coord_flip() +
  labs(
    title = "Prophylactic Antibiotic Use Across Age Groups",
    x = "Age Group",
    y = "Proportion of Patients",
    fill = "Indication"
  ) +
  theme_bw(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 10),
    axis.title.y = element_text(face = "bold"),
    axis.title.x = element_text(face = "bold"),
    axis.text.y = element_text(face = "bold", size = 10),
    legend.position = "bottom",
    legend.title = element_text(face = "bold")
  )

```

<div style='background-color: #f8f9fa; padding: 10px; border-left: 5px solid #17a2b8;'>
  <strong>💡 Note:</strong> This analysis further includes <strong>adult patients</strong> receiving <strong>empiric antibiotics</strong> for the sole purpose of <strong>surgical prophylaxis</strong>, thereby excluding other prophylactics.
  <br>
</div>

