---
title: "[7] Bone & Joint Infection (BJI): WHO AWaRe QIs analysis against gPPS data"
author: "CNPI AMR"
date: "Last compiled on `r format(Sys.time(), '%A %d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    theme: flatly
    df_print: paged
    highlight: tango
    fig_width: 10
    fig_height: 6
    fig_caption: true
    code_folding: hide
editor_options:
  markdown:
    wrap: 72
---

<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
  📊 Report Overview
</h1>
<p style="font-size: 1.15em; color: #444; margin-top: -0.4em; margin-bottom: 1em;">
This report presents a summary of the AWaRe-based quality indicator analysis based on gPPS inpatient data for Bone & Joint Infections (BJIs).

</p>


This analytical script implements **WHO AWaRe (Access, Watch, Reserve)** antibiotic use **quality indicators (QIs)** for treating **BJI** in adult inpatients with **community-acquired infections (CAIs)**. It utilises standardised data from the Global PPS (gPPS), specifically extracted from Excel-based outputs received by participating hospitals.

<div style="background-color: #e9f7fa; border-left: 6px solid #17a2b8; padding: 12px; margin-top: 20px; margin-bottom: 20px;">
<strong>Bone & Joint Infections</strong> (Based on WHO AWaRe book)<br>
▸ <strong>gPPS diagnostic code:</strong> <code>BJ</code><br>
▸ <strong>gPPS definition:</strong> Includes Septic arthritis (including prosthetic joint), osteomyelitis
</div>

The aim is to assess the appropriateness of **empirical antibiotic prescribing** for BJIs, benchmarked against WHO AWaRe Book, and to provide structured feedback at both the hospital and ward levels. These insights support **antimicrobial stewardship efforts** by highlighting patterns of suboptimal prescribing and identifying opportunities for targeted quality improvement.

---


<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
🎯 WHO AWaRe QIs for BJIs
</h2>


Within the scope of the gPPS data structure, **three** QIs have been identified as compatible for evaluating BJIs-related empirical antibiotic prescriptions in adults with CAIs:


<div style="background-color: #e9f7fa; border-left: 6px solid #17a2b8; padding: 12px; margin-top: 20px; margin-bottom: 20px;">
1. <strong>H_OAI_ACCESS_ABX</strong>: Proportion of patients presenting with BJIs (e.g. Acute Bacterial Osteomyelitis or Septic Arthritis) given IV AWaRe Book Access antibiotics.<br><br>
2. <strong>H_OAI_WATCH_ABX</strong>: Proportion of patients presenting with BJIs (e.g. Acute Bacterial Osteomyelitis or Septic Arthritis) given IV AWaRe Book Watch antibiotics.<br><br>
3. <strong>H_OAI_APPROP_DOSAGE</strong>: Proportion of patients presenting with BJIs (e.g. Acute Bacterial Osteomyelitis or Septic Arthritis) prescribed the recommended total daily dose of IV antibiotics according to the WHO AWaRe Book.

</div>


---

<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
💬 General Notes:
</h2>

- Analysis includes only **adult patients (≥18 years)** with **CAIs** on **empirical** treatment.

- **Intravenous (IV) administration** was inferred using the gPPS `"Route"` code `"P"` (Parenteral), recognizing that it may include other parenteral routes but predominantly indicates IV use in empirical clinical practice.

- It was assumed that **WHO recommendations for BJIs** align with the gPPS diagnostic code **`BJ`**; therefore, these cases were assessed using the WHO AWaRe classification.

- **Quality Indicators (QIs)** were mapped and interpreted based on clinical assumptions aligning WHO Book with the available **gPPS diagnostic codes**.

---


<div style="background-color: #fff4e5; border-left: 6px solid #ffc107; padding: 12px; margin-top: 10px;"> 💡 <strong>Reminder:</strong> Caution is advised when interpreting results from small sample sizes (<10 patients) </div> 


<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
🔍 Initial Data Check
</h1>

This section assesses whether there are enough eligible cases to support meaningful analysis.

```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}
rm(list = ls()) #clear global environment

# Define required packages
packages <- c(
  "dplyr", 
  "tidyverse", 
  "readxl", 
  "glue",
  "purrr",
  "tidyr",
  "scales",
  "htmltools", 
  "ggtext", 
  "forcats",
  "kableExtra"
)

# Install missing packages
new_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
if (length(new_packages)) install.packages(new_packages)

# Load all packages
invisible(lapply(packages, library, character.only = TRUE))

# Read the sheets (Patient & Department forms)
data_info <- read_excel(
  "HA-Global-PPS_example_dummy data.xlsx",
  sheet = "Survey",
  col_types = c("guess", "date", "guess", "date")  # to read dates 
)
data_deps <- read_excel("HA-Global-PPS_example_dummy data.xlsx", sheet = "Department forms")
data_patients_all <- read_excel("HA-Global-PPS_example_dummy data.xlsx", sheet = "Patient forms")
data_lookup <- read_excel("QIs-Lookup.xlsx")


# Select the needed data and merge the sheets to create a simpler version.
data_patients <- data_patients_all %>%
  select("Survey Number", "Department name", "Age years", "Weight", "ATC5", "Single Unit Dose", "Unit", "N Doses/day", "Route", "AWaRe", "Diagnosis code", "Indication", "Treatment")

data_patients[data_patients==""]<-NA     # makes all empty spaces to N/A

data_patients <- data_patients %>%
  mutate(
    AWaRe = ifelse(
      toupper(AWaRe) == "NOT_RECOMMENDED",
      "NOT RECOMMENDED",
      AWaRe
    )
  )


AWaRe_abx <- c("ACCESS", "WATCH", "RESERVE", "NOT RECOMMENDED", "UNCLASSIFIED")


#  Check if sufficient eligible Bone & Joint Infection cases are available 


# Flag eligible patients for Community-Acquired Bone & Joint Infection in Adults on Empirical Treatment
data_BJ <- data_patients %>%
  filter(`Diagnosis code` == "BJ") %>%
  mutate(
    Route = toupper(Route),
    AWaRe_compatible = ifelse(
      `Age years` >= 18 & Indication == "CAI" & Treatment == "EMPIRICAL" & AWaRe %in% AWaRe_abx,
      TRUE, FALSE
    )
  )

# Count eligible unique patients
eligible_BJ_n <- data_BJ %>%
  filter(AWaRe_compatible) %>%
  distinct(`Survey Number`) %>%
  nrow()

# Format survey dates (assuming they are in data_info)
survey_start <- format(data_info[[2]][3], "%d %b %Y")
survey_end <- format(data_info[[4]][3], "%d %b %Y")

# HTML feedback summary for BJI
html_feedback <- HTML(glue(
"<div style='background-color: #f0f8ff; border: 1px solid #add8e6; padding: 15px; border-radius: 5px; font-family: sans-serif;'>

  <p style='margin-bottom: 10px;'>
    <strong>📅 Survey period:</strong> {survey_start} to {survey_end}
  </p>

  <p>
    This script applies <strong>WHO AWaRe Quality Indicators</strong> to adult inpatients who received empirical antibiotics for community-acquired bone and joint infections (BJIs).
  </p>

  <ul>
    <li><strong>Diagnostic code:</strong> BJ</li>
    <li><strong>Total eligible cases:</strong> {eligible_BJ_n}</li>
  </ul>

  {if(eligible_BJ_n == 0){
    '<div style=\"background-color:#fff3cd; border: 1px solid #ffeeba; padding: 10px; border-radius: 3px; margin-top: 10px;\">
      <strong>🚫 No eligible cases found:</strong> There were no eligible cases for evaluation during this survey period. Please verify data availability.
    </div>'
  } else if(eligible_BJ_n < 10){
    '<div style=\"background-color:#ffe0e0; border: 1px solid #ffb3b3; padding: 10px; border-radius: 3px; margin-top: 10px;\">
      <strong>⚠️ Caution:</strong> Few eligible cases detected. Interpret results with caution.
    </div>'
  } else {
    '<div style=\"background-color:#e0ffe0; border: 1px solid #b3ffb3; padding: 10px; border-radius: 3px; margin-top: 10px;\">
      <strong>✅ Good to go!</strong> Sufficient eligible cases available to proceed with full evaluation.
    </div>'
  }}

</div>"
))

# Render feedback
htmltools::browsable(html_feedback)


```

***

<hr style="border-top: 3px dashed #28a745; margin-top: 25px; margin-bottom: 15px;">


<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
🧾 Summary of BJI Eligible Patients for QI Assessment
</h1>

Eligible patients for **WHO AWaRe QI** assessment are defined as **adult inpatients (≥18 years)** who received **empirical antibiotics** for **CA-BJI**.

This section presents both **prescription-level** and **patient-level** summaries to establish how much of the dataset is relevant for QI evaluation. It helps frame the proportion of all prescriptions that are relevant to CA-BJI.



<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
👥 Patient-Level Summary
</h2>

This table reports on unique patients in each eligibility group. It reflects the clinical burden of BJI and the proportion of patients suitable for QI evaluation.

<div style="background-color: #f8f9fa; border-left: 5px solid #17a2b8; padding: 12px; margin-top: 10px;">

<strong>📊 Summary:</strong><br>
Total number of patients on antibiotics: <strong>`r data_patients %>% filter(AWaRe %in% AWaRe_abx) %>% distinct(.data[["Survey Number"]]) %>% nrow()`</strong><br>
Total number of eligible patients on antibiotics: <strong>`r data_patients %>% filter(.data[["Age years"]] >= 18, Indication == "CAI", AWaRe %in% AWaRe_abx, Treatment == "EMPIRICAL", .data[["Diagnosis code"]] == "BJ") %>% distinct(.data[["Survey Number"]]) %>% nrow()`</strong>

</div>


```{r echo=FALSE, message=FALSE, warning=FALSE}
# Total unique patients on antibiotics
total_patients <- data_patients %>%
  filter(AWaRe %in% AWaRe_abx) %>%
  distinct(`Survey Number`) %>%
  nrow()

# Patient-level summary
patient_summary <- data.frame(
  Category = c(
    "Number of adult patients (≥18 years) who received empirical antibiotic treatment for CAI",
    "Number of all patients with a diagnosis of BJI on any antibiotics",
    "**Number of eligible patients:** Adult patients (≥18 years) with a diagnosis of CA-BJI who were treated empirically with antibiotics"
  ),
  Count = c(
    data_patients %>%
      filter(`Age years` >= 18, Indication == "CAI", Treatment == "EMPIRICAL", AWaRe %in% AWaRe_abx) %>%
      distinct(`Survey Number`) %>%
      nrow(),
    data_patients %>%
      filter(`Diagnosis code` == "BJ", AWaRe %in% AWaRe_abx) %>%
      distinct(`Survey Number`) %>%
      nrow(),
    data_patients %>%
      filter(`Age years` >= 18, Indication == "CAI", Treatment == "EMPIRICAL", `Diagnosis code` == "BJ", AWaRe %in% AWaRe_abx) %>%
      distinct(`Survey Number`) %>%
      nrow()
  )
) %>%
  mutate(
    Percent = sprintf("%.1f%%", 100 * Count / total_patients)
  )

# Show table
knitr::kable(
  patient_summary,
  col.names = c("Patient Category", "Number of Patients", "Proportion of All Patients"),
  format = "html",
  align = "lcr"  # Left-align category, center number, right-align proportion
) %>%
  kableExtra::kable_styling(
    full_width = FALSE,
    bootstrap_options = c("striped", "hover", "condensed"),
    font_size = 13
  ) %>%
  kableExtra::column_spec(2:3, width = "8em")  

```



<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📑 Prescription-Level Summary
</h2>

<div style="background-color: #f8f9fa; border-left: 5px solid #17a2b8; padding: 12px; margin-top: 10px;">

<strong>📊 Summary:</strong><br>
Total number of antibiotic prescriptions: <strong>`r data_patients %>% filter(AWaRe %in% AWaRe_abx) %>% nrow()`</strong><br>
Total number of eligible antibiotic prescriptions: <strong>`r data_patients %>% filter(.data[["Age years"]] >= 18, Indication == "CAI", AWaRe %in% AWaRe_abx, Treatment == "EMPIRICAL", .data[["Diagnosis code"]] == "BJ") %>% nrow()`</strong>

</div>


```{r echo=FALSE, message=FALSE, warning=FALSE}
# Total prescriptions
total_prescriptions <- data_patients %>%
  filter(AWaRe %in% AWaRe_abx) %>%
  nrow()

# Prescription summary table
prescription_summary <- data.frame(
  Category = c(
    "Number of empirical antibiotic prescriptions administered to adult patients (≥18 years) for CAI",
    "Number of all antibiotic prescriptions for patients diagnosed with BJI",
    "**Number of eligible antibiotic prescriptions:** antibiotics empirically prescribed for adult patients (≥18 years) with CA-BJI"
  ),
  Count = c(
    data_patients %>% filter(`Age years` >= 18, Indication == "CAI", Treatment == "EMPIRICAL", AWaRe %in% AWaRe_abx) %>% nrow(),
    data_patients %>% filter(`Diagnosis code` == "BJ", AWaRe %in% AWaRe_abx) %>% nrow(),
    data_patients %>% filter(`Age years` >= 18, Indication == "CAI", Treatment == "EMPIRICAL", `Diagnosis code` == "BJ", AWaRe %in% AWaRe_abx) %>% nrow()
  )
) %>%
  mutate(
    Percent = sprintf("%.1f%%", 100 * Count / total_prescriptions)
  )

# Display table
knitr::kable(
  prescription_summary,
  col.names = c("Prescription Category", "Number of Prescriptions", "Proportion of All Prescriptions"),
  format = "html",
  align = "lcr"  # Left-align category, center number, right-align proportion
) %>%
  kableExtra::kable_styling(
    full_width = FALSE,
    bootstrap_options = c("striped", "hover", "condensed"),
    font_size = 13
  ) %>%
  kableExtra::column_spec(2:3, width = "8em") 

```

***

<hr style="border-top: 3px dashed #28a745; margin-top: 25px; margin-bottom: 15px;">


<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📘 WHO AWaRe-QIs Overview
</h1>

This script evaluates **THREE** WHO AWaRe indicators:


<div style="background-color: #e9f7fa; border-left: 6px solid #17a2b8; padding: 12px; margin-top: 20px; margin-bottom: 20px;">
1. <strong>H_OAI_ACCESS_ABX</strong>: Proportion of patients presenting with BJIs (e.g. Acute Bacterial Osteomyelitis or Septic Arthritis) given IV AWaRe Book Access antibiotics.<br><br>
2. <strong>H_OAI_WATCH_ABX</strong>: Proportion of patients presenting with BJIs (e.g. Acute Bacterial Osteomyelitis or Septic Arthritis) given IV AWaRe Book Watch antibiotics.<br><br>
3. <strong>H_OAI_APPROP_DOSAGE</strong>: Proportion of patients presenting with BJIs (e.g. Acute Bacterial Osteomyelitis or Septic Arthritis) prescribed the recommended total daily dose of IV antibiotics according to the WHO AWaRe Book.

</div>

<div style="background-color: #f8f9fa; border-left: 5px solid #17a2b8; padding: 12px; margin-top: 10px; margin-bottom: 10px;">
<strong>🔍 WHO AWaRe Book Recommendation:</strong><br><br>

<ul style="list-style-type: none; padding-left: 0; line-height: 1.8;">
  <li><strong>Option 1:</strong> Cloxacillin (2 g q6h IV)</li>
  <li><strong>Option 2:</strong> Amoxicillin + clavulanic acid (1 g + 200 mg q8h IV)</li>
  <li><strong>Option 3:</strong> Cefazolin (2 g q8h IV)</li>
  <li><strong>Option 4:</strong> Cefotaxime (2 g q8h IV)</li>
  <li><strong>Option 5:</strong> Ceftriaxone (2 g q24h IV)</li>
  <li><strong>Option 6:</strong> Clindamycin (600 mg q8h IV/ORAL)</li>
</ul>
</div>


<div style="background-color: #fff3cd; border-left: 5px solid #ffc107; padding: 12px; margin-top: 10px; margin-bottom: 18px;">
<strong>🩺 WHO AWaRe Notes:</strong>
<ul>
  <li>The intravenous route is preferred at least in the first week of treatment</li>
  <li>Step down to oral treatment is based on improvement</li>
  <li>If cloxacillin is unavailable, any other IV antistaphylococcal penicillin could be used. </li>
  <li>A higher dose (e.g. 12 g/day) could be considered given the concerns with bone penetration.</li>
  <li>Ceftriaxone or cefotaxime are the preferred options if invasive non-typhoidal Salmonella or Enterobacterales infection is suspected</li>
    <li>Acceptable option for community-acquired-MRSA if MRSA is susceptible or in settings where MRSA maintains high levels of susceptibility to clindamycin, otherwise consider vancomycin</li>
</ul>
</div>

<hr style="border-top: 3px dashed #28a745; margin-top: 25px; margin-bottom: 15px;">

***

<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📌 Indicator 1 & 2 - IV Access & Watch Antibiotic Use
</h1>

This section evaluates two WHO AWaRe indicators:

> **H_OAI_ACCESS_ABX:** Proportion of patients presenting with BJIs (e.g. Acute Bacterial Osteomyelitis or Septic Arthritis) given **IV AWaRe Book Access antibiotics**.

> **H_OAI_WATCH_ABX:** Proportion of patients presenting with BJIs (e.g. Acute Bacterial Osteomyelitis or Septic Arthritis) given **IV AWaRe Book Watch antibiotics**.

***

<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📝 Summary of Access/Watch Antibiotic Use
</h2>

This section summarizes use of IV Access/Watch antibiotics for patients with BJIs across hospital departments

 
```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}
# Filter BJ patients & flag eligibility
data_BJ <- data_patients %>%
  filter(`Diagnosis code` == "BJ") %>%
  mutate(
    Route = toupper(Route),
    Eligible = ifelse(
      `Age years` >= 18 & Indication == "CAI" & Treatment == "EMPIRICAL" & AWaRe %in% AWaRe_abx,
      TRUE, FALSE
    )
  )

# Keep eligible patients only
data_BJ_eligible <- data_BJ %>%
  filter(Eligible == TRUE)

# Total patient counts
total_BJ <- data_BJ %>% distinct(`Survey Number`) %>% nrow()
eligible_BJ <- data_BJ_eligible %>% distinct(`Survey Number`) %>% nrow()

# Handle case of no eligible patients
if (eligible_BJ == 0 || is.na(eligible_BJ)) {
  final_summary_html <- HTML(
    "<div style='background-color: #fff3cd; border-left: 5px solid #ffc107; padding: 14px; margin-top: 10px;'>
    ⚠️ <strong>No summary available</strong> — there are currently no eligible patients with antibiotic data for assessment.<br><br>
    <em>This may indicate that no patients received antibiotics, or none met inclusion criteria.</em>
    </div>"
  )
  htmltools::browsable(final_summary_html)

} else {

  # Summarise whether patient received each IV type
  summary_iv_aware <- data_BJ_eligible %>%
    group_by(`Survey Number`, `Department name`) %>%
    summarise(
      IV_ACCESS = any(Route == "P" & AWaRe == "ACCESS"),
      IV_WATCH  = any(Route == "P" & AWaRe == "WATCH"),
      IV_OTHER  = any(Route == "P" & !(AWaRe %in% c("ACCESS", "WATCH"))),
      ANY_IV    = any(Route == "P"),
      .groups = "drop"
    ) %>%
    mutate(
      Not_IV = !ANY_IV
    )

  # Department-level summary
  summary_iv_dept <- summary_iv_aware %>%
    group_by(`Department name`) %>%
    summarise(
      Eligible     = n(),
      N_IV_ACCESS  = sum(IV_ACCESS),
      N_IV_WATCH   = sum(IV_WATCH),
      N_IV_OTHER   = sum(IV_OTHER),
      N_Not_IV     = sum(Not_IV),
      Prop_ACCESS  = round(100 * N_IV_ACCESS / Eligible, 1),
      Prop_WATCH   = round(100 * N_IV_WATCH / Eligible, 1),
      Prop_OTHER   = round(100 * N_IV_OTHER / Eligible, 1),
      Prop_Not_IV  = round(100 * N_Not_IV / Eligible, 1),
      .groups = "drop"
    )

  # Hospital-level summary
  summary_iv_total <- summary_iv_aware %>%
    summarise(
      `Department name` = "Hospital-Wide",
      Eligible     = n(),
      N_IV_ACCESS  = sum(IV_ACCESS),
      N_IV_WATCH   = sum(IV_WATCH),
      N_IV_OTHER   = sum(IV_OTHER),
      N_Not_IV     = sum(Not_IV),
      Prop_ACCESS  = round(100 * N_IV_ACCESS / Eligible, 1),
      Prop_WATCH   = round(100 * N_IV_WATCH / Eligible, 1),
      Prop_OTHER   = round(100 * N_IV_OTHER / Eligible, 1),
      Prop_Not_IV  = round(100 * N_Not_IV / Eligible, 1)
    )

  # Combine summaries
  summary_iv_final <- bind_rows(summary_iv_total, summary_iv_dept)

  # Intro block
  intro_text <- glue::glue(
    "<div style='background-color: #f8f9fa; border-left: 5px solid #17a2b8; padding: 14px; margin-top: 10px; margin-bottom: 10px;'>
    💊 <strong>Denominator:</strong> Number of eligible patients with any BJI (<strong>{eligible_BJ}</strong> out of {total_BJ})
    </div><br><br>
    <strong>Summary:</strong><br><br>"
  )

  # Build formatted summary blocks
  formatted_blocks <- summary_iv_final %>%
    mutate(block = pmap_chr(
      list(
        `Department name`,
        Prop_ACCESS, N_IV_ACCESS,
        Prop_WATCH, N_IV_WATCH,
        Prop_OTHER, N_IV_OTHER,
        Prop_Not_IV, N_Not_IV,
        Eligible
      ),
      function(dept, access_p, access_n, watch_p, watch_n, other_p, other_n, notiv_p, notiv_n, total_n) {
        color <- if (dept == "Hospital-Wide") "#0072B2" else "#6c757d"
        bg <- if (dept == "Hospital-Wide") "#f0f0f0" else "#ffffff"

        glue::glue(
          "<div style='background-color: {bg}; border-left: 5px solid {color}; padding: 14px; margin-bottom: 20px;'>

          <strong>🏥 {dept}</strong> <span style='color: #888;'>(n = {total_n} patients)</span><br><br>

          <ul style='margin-left: 1.2em; line-height: 1.8; padding-left: 0; list-style-type: none;'>
            <li>
              <span style='display: inline-block; background-color: #1b9e77; color: white; border-radius: 50%; width: 22px; height: 22px; text-align: center; line-height: 22px; font-size: 12px; margin-right: 8px;'>1</span>
              <strong>Received IV ACCESS antibiotic</strong>: <strong>{scales::percent(access_p / 100, accuracy = 0.1)}</strong> ({access_n} out of {total_n})
            </li>
            <li>
              <span style='display: inline-block; background-color: #ff7f00; color: white; border-radius: 50%; width: 22px; height: 22px; text-align: center; line-height: 22px; font-size: 12px; margin-right: 8px;'>2</span>
              <strong>Received IV WATCH antibiotic</strong>: <strong>{scales::percent(watch_p / 100, accuracy = 0.1)}</strong> ({watch_n} out of {total_n})
            </li>
            <li>
              <span style='display: inline-block; background-color: #e41a1c; color: white; border-radius: 50%; width: 22px; height: 22px; text-align: center; line-height: 22px; font-size: 12px; margin-right: 8px;'>3</span>
              <strong>Received IV OTHER AWaRe antibiotic</strong>: <strong>{scales::percent(other_p / 100, accuracy = 0.1)}</strong> ({other_n} out of {total_n})
            </li>
            <li>
              <span style='display: inline-block; background-color: #6c757d; color: white; border-radius: 50%; width: 22px; height: 22px; text-align: center; line-height: 22px; font-size: 12px; margin-right: 8px;'>4</span>
              <strong>Did NOT receive any IV antibiotic</strong>: <strong>{scales::percent(notiv_p / 100, accuracy = 0.1)}</strong> ({notiv_n} out of {total_n})
            </li>
          </ul>

          </div>"
        )
      }
    ))

  # Reorder Hospital-Wide first
  formatted_blocks <- formatted_blocks %>%
    mutate(order = ifelse(`Department name` == "Hospital-Wide", 0, 1)) %>%
    arrange(order, `Department name`) %>%
    select(-order)

  # Final output
  final_summary_html <- HTML(paste0(intro_text, paste(formatted_blocks$block, collapse = "\n")))
  htmltools::browsable(final_summary_html)
}



```

***


<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📈 Antibiotic Prescription by AWaRe Classification
</h2>

This visual summarises the proportion of antibiotic prescription for BJIs across hospital departments by WHO AWaRe Classification (Access, Watch, Reserve)


```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}
#  Always define route_levels 
route_levels <- c("IV ACCESS", "IV WATCH", "IV OTHER", "No IV")

#  Ensure summary_iv_final exists even if no eligible patients 
if (eligible_BJ == 0) {

  dept_list <- sort(unique(data_BJ$`Department name`))

  summary_iv_final <- expand_grid(
    `Department name` = dept_list
  ) %>%
    mutate(
      Eligible = 0,
      N_IV_ACCESS = 0,
      N_IV_WATCH = 0,
      N_IV_OTHER = 0,
      N_Not_IV = 0
    )
}


#  Plot construction (always runs) 
all_combos <- expand_grid(
  `Department name` = sort(unique(summary_iv_final$`Department name`)),
  Route = route_levels
)

plot_data <- summary_iv_final %>%
  select(`Department name`, Eligible,
         `IV ACCESS` = N_IV_ACCESS,
         `IV WATCH`  = N_IV_WATCH,
         `IV OTHER`  = N_IV_OTHER,
         `No IV`     = N_Not_IV) %>%
  pivot_longer(
    cols = c(`IV ACCESS`, `IV WATCH`, `IV OTHER`, `No IV`),
    names_to = "Route",
    values_to = "Count"
  ) %>%
  right_join(all_combos, by = c("Department name", "Route")) %>%
  mutate(
    Count = replace_na(Count, 0)
  ) %>%
  group_by(`Department name`) %>%
  mutate(
    Total = sum(Count),
    Proportion = ifelse(Total > 0, Count / Total, 0),
    Label = ifelse(Proportion > 0.05, paste0(round(Proportion * 100), "%\n(n=", Count, ")"), "")
  ) %>%
  ungroup() %>%
  mutate(
    PlotLabel = ifelse(
      `Department name` == "Hospital-Wide",
      "<b style='color:#0072B2;'>Hospital-Wide</b>",
      `Department name`
    ),
    PlotLabel = factor(
      PlotLabel,
      levels = c(
        "<b style='color:#0072B2;'>Hospital-Wide</b>",
        sort(setdiff(unique(`Department name`), "Hospital-Wide"))
      )
    ),
    Route = factor(Route, levels = route_levels)
  )

#  Draw the plot 
ggplot(plot_data, aes(x = 2, y = Proportion, fill = Route)) +
  geom_bar(stat = "identity", width = 0.1) +
  coord_polar(theta = "y") +
  facet_wrap(~ PlotLabel, nrow = 2, strip.position = "bottom", drop = FALSE) +
  geom_text(aes(label = Label), position = position_stack(vjust = 0.5), size = 3, color = "white") +
  scale_fill_manual(
    breaks = route_levels,
    values = c(
      "IV ACCESS" = "#1B9E77",
      "IV WATCH"  = "#ff7f00",
      "IV OTHER"  = "#E41A1C",
      "No IV"     = "#999999"
    ),
    drop = FALSE
  ) +
  theme_void(base_size = 10) +
  theme(
    strip.text = ggtext::element_markdown(face = "bold", size = 9),
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
    panel.spacing = unit(1, "lines")
  ) +
  labs(
    title = "IV Antibiotic Use by AWaRe Category (BJIs)",
    fill = "Group"
  )


```


<div style='background-color: #f8f9fa; padding: 10px; border-left: 5px solid #17a2b8;'>
  <strong>💡 Note:</strong> The AWaRe classification divides antibiotics into three categories: Access, Watch, and Reserve. Access antibiotics are first-line treatments with a low risk of resistance, typically recommended for common infections. Watch antibiotics are associated with a higher risk of resistance and require careful monitoring. Reserve antibiotics are reserved for critical cases involving resistant infections, typically used only when other options are ineffective </strong>.
  <br>
</div>
***

<hr style="border-top: 3px dashed #28a745; margin-top: 25px; margin-bottom: 15px;">

<h1 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📌 Indicator 3 – IV Antibiotic Appropriateness 
</h1>

> **H_OAI_APPROP_DOSAGE:** Proportion of patients presenting with BJIs (e.g. Acute Bacterial Osteomyelitis or Septic Arthritis) prescribed the recommended total daily dose of IV antibiotics according to the WHO AWaRe Book.



```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}

#  Data preparation: antibiotic choice appropriateness

#  Prepare the data (Select BJ data only)
data_BJ_choice <- data_patients %>%
  filter(`Diagnosis code` == "BJ") %>%
  mutate(
    Route = toupper(Route),
    AWaRe_compatible = ifelse(
      `Age years` >= 18 & Indication == "CAI" & Treatment == "EMPIRICAL" & AWaRe %in% AWaRe_abx,
      TRUE, FALSE
    )
  )

#  Lookup ABX names for QI
lookup_names <- data_lookup %>%
  filter(Code == "H_OAI_APPROP_DOSAGE") %>%
  select(starts_with("ABX-ATC")) %>%
  unlist(use.names = FALSE)

#  Flag matched prescriptions
data_BJ_choice <- data_BJ_choice %>%
  mutate(
    Drug_Match = ATC5 %in% lookup_names
  )

#  Extract lookup info 
lookup_BJ_choice <- data_lookup %>%
  filter(Code == "H_OAI_APPROP_DOSAGE")

# Create long format from lookup
lookup_long <- tibble(
  Drug = unlist(lookup_BJ_choice %>% select(starts_with("ABX-ATC")), use.names = FALSE),
  Choice = unlist(lookup_BJ_choice %>% select(starts_with("ABX-CHOICE")), use.names = FALSE)
) %>%
  filter(!is.na(Drug))  # Remove empty rows

# Merge choice info with patient-level data
data_BJ_choice <- data_BJ_choice %>%
  left_join(lookup_long, by = c("ATC5" = "Drug"))

# Add Department info to patient summary
patient_summary_BJ <- data_BJ_choice %>%
  filter(AWaRe_compatible) %>%
  group_by(`Survey Number`, `Department name`) %>% 
  summarise(
    
    All_ABX = list(unique(ATC5)),

    # Match flags
    Match_1 = any(ATC5 == lookup_names[1]),
    Match_2 = any(ATC5 == lookup_names[2]),
    Match_3 = any(ATC5 == lookup_names[3]),
    Match_4 = any(ATC5 == lookup_names[4]),
    Match_5 = any(ATC5 == lookup_names[5]),
    Match_6 = any(ATC5 == lookup_names[6]),
    
    # Route-specific match flags
    Match_1_P = any(ATC5 == lookup_names[1] & Route == "P"),
    Match_2_P = any(ATC5 == lookup_names[2] & Route == "P"),
    Match_3_P = any(ATC5 == lookup_names[3] & Route == "P"),
    Match_4_P = any(ATC5 == lookup_names[4] & Route == "P"),
    Match_5_P = any(ATC5 == lookup_names[5] & Route == "P"),
    Match_6_P = any(ATC5 == lookup_names[6] & Route == "P"),
    
    N_ABX = n_distinct(ATC5),
    Any_IV = any(Route == "P"),
    Any_Oral = any(Route == "O"),
    .groups = "drop"
  ) %>%
  rowwise() %>%
  mutate(
    Num_Recommended_P = sum(c_across(Match_1_P:Match_6_P)),

    # Fully appropriate: only one antibiotic, and it's recommended
    Appropriate = Num_Recommended_P == 1 & N_ABX == 1,

    # Partial appropriate: ≥1 recommended drug, but given with others
    Partial_Appropriate = Num_Recommended_P >= 1 & N_ABX > 1,

    # Inappropriate IV use (no recommended drugs via IV)
    No_Appropriate = Any_IV & !Appropriate & !Partial_Appropriate,
    
    # Oral antibiotics use
    Oral_antibiotics = Any_Oral & !Appropriate & !Partial_Appropriate & !No_Appropriate,
    
    # All other inappropriate cases
    No_Appropriate_others = !Appropriate & !Partial_Appropriate & !No_Appropriate & !Oral_antibiotics
  ) %>%
  ungroup()

# Get not eligible patients
not_eligible_patients_BJ <- data_BJ_choice %>%
  group_by(`Survey Number`, `Department name`) %>%
  summarise(Ineligible = all(AWaRe_compatible == FALSE), .groups = "drop") %>%
  filter(Ineligible)

# Reshape eligible indicators to long format
eligible_long_BJ <- patient_summary_BJ %>%
  select(`Survey Number`, `Department name`, Appropriate, Partial_Appropriate, No_Appropriate, Oral_antibiotics, No_Appropriate_others) %>%
  pivot_longer(
    cols = -c(`Survey Number`, `Department name`),
    names_to = "Indicator",
    values_to = "Value"
  ) %>%
  filter(Value) %>%
  group_by(`Department name`, Indicator) %>%
  summarise(Patients = n(), .groups = "drop")

# Create "Not Eligible" summary
ineligible_summary_BJ <- not_eligible_patients_BJ %>%
  count(`Department name`) %>%
  mutate(Indicator = "Not_Eligible") %>%
  rename(Patients = n)

# Combine all indicator data
combined_BJ <- bind_rows(eligible_long_BJ, ineligible_summary_BJ)

# Expand all department-indicator combinations
all_combos_BJ <- expand_grid(
  `Department name` = unique(combined_BJ$`Department name`),
  Indicator = c("Appropriate", "Partial_Appropriate", "No_Appropriate", "Oral_antibiotics", "No_Appropriate_others", "Not_Eligible")
)

# Ensure all categories appear with 0 if missing
qi_long_BJ <- all_combos_BJ %>%
  left_join(combined_BJ, by = c("Department name", "Indicator")) %>%
  mutate(Patients = replace_na(Patients, 0))

# Department totals
dept_totals_BJ <- qi_long_BJ %>%
  group_by(`Department name`) %>%
  summarise(Total = sum(Patients), .groups = "drop")

# Calculate proportions and clean labels
qi_summary_BJ <- qi_long_BJ %>%
  left_join(dept_totals_BJ, by = "Department name") %>%
  mutate(
    Indicator = case_when(
      Indicator == "Appropriate" ~ "Received recommended IV antibiotics",
      Indicator == "Partial_Appropriate" ~ "Partially received recommended IV antibiotics",
      Indicator == "No_Appropriate" ~ "Received IV antibiotics not among recommended options",
      Indicator == "Oral_antibiotics" ~ "Received oral antibiotics",
      Indicator == "No_Appropriate_others" ~ "Received other non-IV/oral antibiotics",
      Indicator == "Not_Eligible" ~ "Not eligible for AWaRe BJI QIs",
      TRUE ~ Indicator
    ),
    Proportion = round(Patients / Total, 4)
  )

# Add Hospital-Wide totals
hospital_data_BJ <- qi_summary_BJ %>%
  group_by(Indicator) %>%
  summarise(Patients = sum(Patients), .groups = "drop") %>%
  mutate(`Department name` = "Hospital-Wide")

# Combine with department-level data
qi_summary_BJ <- bind_rows(qi_summary_BJ, hospital_data_BJ)

# Recalculate total and proportion for Hospital-Wide
qi_summary_BJ <- qi_summary_BJ %>%
  group_by(`Department name`) %>%
  mutate(
    Total = sum(Patients),
    Proportion = round(Patients / Total, 4)
  ) %>%
  ungroup()

```

<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📈 Antibiotic Choice Appropriateness for BJIs
</h2>
 
This visual summarises the proportion of antibiotic appropriateness for BJIs across hospital departments based on WHO AWaRe Book

 
```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}

# Define label and color lookup
indicator_labels <- c(
  "Appropriate"               = "Received recommended IV antibiotics",
  "Partial_Appropriate"    = "Partially received recommended IV antibiotics",
  "No_Appropriate"            = "Received IV antibiotics not among recommended options",
  "Oral_antibiotics"          = "Received oral antibiotics",
  "No_Appropriate_others"     = "Received other non-IV/oral antibiotics",
  "Not_Eligible"              = "Not eligible for AWaRe BJI QIs"
)

drug_choice_colors <- c(
  "Received recommended IV antibiotics"             = "#1F77B4",
  "Partially received recommended IV antibiotics"         = "#4FA9DC",
  "Received IV antibiotics not among recommended options"         = "#EF476F",
  "Received oral antibiotics"                       = "#F9D99E",
  "Received other non-IV/oral antibiotics"      = "#D3D3D3",
  "Not eligible for AWaRe BJI QIs"             = "#A9A9A9"
)

# Reorder Department + apply markdown formatting for Hospital-Wide
qi_summary_BJ <- qi_summary_BJ %>%
  mutate(
    Indicator = factor(
      Indicator,
      levels = c(
        "Received recommended IV antibiotics",
        "Partially received recommended IV antibiotics",
        "Received IV antibiotics not among recommended options",
        "Received oral antibiotics",
        "Received other non-IV/oral antibiotics",
        "Not eligible for AWaRe BJI QIs"
      )
    ),
    PlotLabel = ifelse(
      `Department name` == "Hospital-Wide",
      "<b style='color:#0072B2;'>Hospital-Wide</b>",
      `Department name`
    ),
    PlotLabel = factor(
      PlotLabel,
      levels = c(
        "<b style='color:#0072B2;'>Hospital-Wide</b>",
        sort(setdiff(unique(`Department name`), "Hospital-Wide"))
      )
    )
  )

# Create the plot
ggplot(qi_summary_BJ, aes(x = PlotLabel, y = Proportion, fill = Indicator)) +

  # Highlight Hospital-Wide bar
  annotate("rect",
           xmin = 0.5, xmax = 1.5, ymin = 0, ymax = 1,
           fill = "gray95", alpha = 0.5) +

  # Stacked proportional bars
  geom_bar(stat = "identity", position = "fill", width = 0.85) +

  # Patient count labels inside bars
  geom_text(
    aes(label = ifelse(Patients > 0, Patients, "")),
    position = position_fill(vjust = 0.5),
    size = 3, color = "black"
  ) +

  # Total n= labels above bars
  geom_text(
    data = qi_summary_BJ %>% distinct(PlotLabel, Total),
    aes(x = PlotLabel, y = 1.05, label = paste0("n=", Total)),
    inherit.aes = FALSE,
    size = 3, color = "gray30", hjust = 0.6
  ) +

  # Manual color scale
  scale_fill_manual(
    values = drug_choice_colors,
    labels = indicator_labels
  ) +

  # Keep vertical bars
  scale_y_continuous(limits = c(0, 1.09), expand = c(0, 0)) +

  # Labels
  labs(
    title = "Antibiotic Choice Appropriateness Summary for BJIs",
    subtitle = "Each bar shows distribution of appropriateness against WHO AWaRe guidelines (n = raw patient counts)",
    x = "Department",
    y = "Proportional Stacked Bars",
    fill = "Treatment Appropriateness Category"
  ) +

  # Aesthetic theme
  theme_minimal(base_size = 8) +
  theme(
    axis.text.x = ggtext::element_markdown(size = 8, angle = 45, hjust = 1),
    axis.text.y = element_text(size = 8),
    axis.title = element_text(face = "bold", size = 10),
    legend.position = "right",
    legend.title = element_text(face = "bold", size = 8),
    legend.text = element_text(size = 8, margin = margin(b = 4)),
    plot.title = element_text(face = "bold", hjust = 0.5, size = 10),
    plot.subtitle = element_text(hjust = 0.5, size = 7, color = "gray30"),
    panel.border = element_rect(color = "gray70", fill = NA, size = 0.8),
    plot.margin = margin(10, 10, 10, 10)
  ) +

  # Legend format: 1 category per row
  guides(
    fill = guide_legend(nrow = 6, byrow = FALSE, title.position = "top")
  )


```

---

<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📈 Antibiotic Choice Appropriateness by AWaRe Classification
</h2>

This visual summarises the proportion of antibiotic appropriateness for BJIs across hospital departments by WHO AWaRe Classification (Access, Watch, Reserve)

 
```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}
# Add Department info to patient summary
patient_summary_AWARE <- data_BJ_choice %>%
  filter(AWaRe_compatible) %>%
  group_by(`Survey Number`, `Department name`, AWaRe) %>%  # Add department here
  summarise(
    N_total = n(),
    N_match = sum(Drug_Match),
    N_p = sum(Route == "P"),
    N_p_match = sum(Route == "P" & Drug_Match),

    # Match flags
    Match_1 = any(ATC5 == lookup_names[1]),
    Match_2 = any(ATC5 == lookup_names[2]),
    Match_3 = any(ATC5 == lookup_names[3]),
    Match_4 = any(ATC5 == lookup_names[4]),
    Match_5 = any(ATC5 == lookup_names[5]),
    Match_6 = any(ATC5 == lookup_names[6]),
    
    # Route-specific match flags
    Match_1_P = any(ATC5 == lookup_names[1] & Route == "P"),
    Match_2_P = any(ATC5 == lookup_names[2] & Route == "P"),
    Match_3_P = any(ATC5 == lookup_names[3] & Route == "P"),
    Match_4_P = any(ATC5 == lookup_names[4] & Route == "P"),
    Match_5_P = any(ATC5 == lookup_names[5] & Route == "P"),
    Match_6_P = any(ATC5 == lookup_names[6] & Route == "P"),
    
    .groups = "drop"
  ) %>%
  mutate(
        Appropriate_IV = (
      (Match_1_P | Match_2_P | Match_3_P | Match_4_P | Match_5_P | Match_6_P) 
    ))


#  Create summary table with Department name
AWaRe_long <- patient_summary_AWARE %>%
  select(`Survey Number`, `Department name`, AWaRe, Appropriate_IV) %>%
  pivot_longer(
    cols = -c(`Survey Number`, `Department name`, AWaRe),
    names_to = "Indicator",
    values_to = "Value"
  ) %>%
  filter(Value) %>%
  group_by(`Department name`, AWaRe, Indicator) %>%
  summarise(Patients = n(), .groups = "drop")

# Calculate total per department
AWaRe_dept_totals <- AWaRe_long %>%
  group_by(`Department name`) %>%
  summarise(Total = sum(Patients), .groups = "drop")

# Final summary table with proportions
AWaRe_long <- AWaRe_long %>%
  left_join(AWaRe_dept_totals, by = "Department name")  %>% 
  mutate (Proportion = round(100 * Patients / Total, 1))


#  Add Hospital Total row 
AWaRe_hospital_data <- AWaRe_long %>%
  group_by(AWaRe) %>%
  summarise(Patients = sum(Patients), .groups = "drop") %>%
  mutate(`Department name` = "Hospital-Wide") %>%
  select(`Department name`, AWaRe, Patients)

# Combine with original data
AWaRe_long <- bind_rows(AWaRe_long, AWaRe_hospital_data)


# Recalculate totals and proportions
AWaRe_long <- AWaRe_long %>%
  group_by(`Department name`) %>%
  mutate(
    Total = sum(Patients),
    Proportion = Patients / Total
  ) %>%
  ungroup()

# Format "Hospital" label to bold
AWaRe_long <- AWaRe_long %>%
  mutate(`Department name` = ifelse(`Department name` == "Hospital-Wide", "Hospital-Wide", `Department name`))
 

# ------ Ploting------

# Set stacking and legend orders
aware_levels_stack <- c("WATCH", "ACCESS")
aware_levels_legend <- c("ACCESS", "WATCH")

# Ensure AWaRe is a factor
AWaRe_long$AWaRe <- factor(AWaRe_long$AWaRe, levels = aware_levels_stack)

# Create full grid of departments × AWaRe levels
all_combos <- expand_grid(
  `Department name` = unique(AWaRe_long$`Department name`),
  AWaRe = aware_levels_stack
)

# Left join to fill in missing combinations with zero
AWaRe_long <- all_combos %>%
  left_join(AWaRe_long, by = c("Department name", "AWaRe")) %>%
  mutate(
    Patients = replace_na(Patients, 0),
    Total = replace_na(Total, 0)
  ) %>%
  group_by(`Department name`) %>%
  mutate(
    Total = sum(Patients),
    Proportion = ifelse(Total > 0, Patients / Total, 0)
  ) %>%
  ungroup()

#  Exclude departments with zero total patients
AWaRe_long <- AWaRe_long %>%
  filter(Total > 0)

# Format Hospital-Wide label to bold
AWaRe_long <- AWaRe_long %>%
  mutate(
    PlotLabel = ifelse(
      `Department name` == "Hospital-Wide",
      "<b style='color:#0072B2;'>Hospital-Wide</b>",
      `Department name`
    ),
    PlotLabel = factor(
      PlotLabel,
      levels = rev(c(
        "<b style='color:#0072B2;'>Hospital-Wide</b>",
        sort(setdiff(unique(`Department name`), "Hospital-Wide"))
      ))
    )
  )

# Build the plot
ggplot(AWaRe_long, aes(x = PlotLabel, y = Proportion, fill = AWaRe)) +
  
  # Highlight Hospital-Wide row
  annotate("rect", xmin = 0.5, xmax = 1.5, ymin = 0, ymax = 1,
           fill = "gray95", alpha = 0.5) +
  
  # Stacked proportional bars
  geom_bar(stat = "identity", position = "fill", width = 0.85) +
  
  # Percent labels inside bars (only if >5%)
  geom_text(
    aes(label = ifelse(Proportion > 0.05, scales::percent(Proportion, accuracy = 1), "")),
    position = position_fill(vjust = 0.5),
    size = 3.5, color = "black"
  ) +
  
  # Total n= labels above bars
  geom_text(
    data = AWaRe_long %>% distinct(PlotLabel, Total),
    aes(x = PlotLabel, y = 1.015, label = paste0("n=", Total)),
    inherit.aes = FALSE,
    size = 3, color = "gray30", hjust = 0
  ) +
  
  # Color scale + legend with all categories shown
  scale_fill_manual(
    breaks = aware_levels_legend,
    values = c(
      "ACCESS" = "#1b9e77",
      "WATCH"  = "#ff7f00"
    ),
    drop = FALSE  # ensure all AWaRe categories appear in legend even if zero
  ) +
  
  # Flip bar orientation
  coord_flip(ylim = c(0, 1.04)) +
  
  # Labels
  labs(
    title = "Use of Recommended IV Antibiotics by AWaRe Classification",
    subtitle = "Proportions by department (percentages shown inside bars)",
    x = "Department",
    y = "Proportion of Patients",
    fill = "AWaRe Classification"
  ) +
  
  # Styling
  theme_minimal(base_size = 12) +
  theme(
    axis.text.y = ggtext::element_markdown(size = 10),  # enables bold Hospital-Wide
    axis.text.x = element_text(size = 10),
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    panel.border = element_rect(color = "gray70", fill = NA),
    legend.position = "bottom",
    legend.title = element_text(face = "bold", size = 9),
    plot.margin = margin(10, 10, 10, 10)
  )


```


***
<div style="background-color: #f8f9fa; border-left: 5px solid #17a2b8; padding: 12px; margin-top: 10px;"> 
  <strong>💡 Note:</strong> The AWaRe classification divides antibiotics into three categories: Access, Watch, and Reserve. Access antibiotics are first-line treatments with a low risk of resistance, typically recommended for common infections. Watch antibiotics are associated with a higher risk of resistance and require careful monitoring. Reserve antibiotics are reserved for critical cases involving resistant infections, typically used only when other options are ineffective </strong>.
  <br>
</div>

---

<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📈 Antibiotic Choice Appropriateness by line of treatment
</h2>

This visual summarises the proportion of antibiotic appropriateness for BJIs across hospital departments by line of treatment (First choice, Second choice)

 
```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}

# Define stacking and legend orders
choice_levels_stack <- c("Second choice", "First choice")
choice_levels_legend <- c("First choice", "Second choice")

# Ensure all choices are present per department (for zeros)
all_combos <- expand_grid(
  `Department name` = unique(data_BJ_choice$`Department name`),
  Choice = choice_levels_stack
)

# Build department-level summary with zeros
choice_summary <- data_BJ_choice %>%
  filter(AWaRe_compatible == TRUE, Route == "P", !is.na(Choice)) %>%
  group_by(`Department name`, Choice) %>%
  summarise(Prescriptions = n(), .groups = "drop") %>%
  right_join(all_combos, by = c("Department name", "Choice")) %>%
  mutate(Prescriptions = replace_na(Prescriptions, 0)) %>%
  group_by(`Department name`) %>%
  mutate(
    Total = sum(Prescriptions),
    Proportion = ifelse(Total > 0, Prescriptions / Total, 0)
  ) %>%
  ungroup() %>%
  filter(Total > 0)  # Exclude departments with zero total prescriptions

# Add Hospital-Wide summary (ensuring all choices included)
hospital_summary <- data_BJ_choice %>%
  filter(AWaRe_compatible == TRUE, Route == "P", !is.na(Choice)) %>%
  group_by(Choice) %>%
  summarise(Prescriptions = n(), .groups = "drop") %>%
  right_join(tibble(Choice = choice_levels_stack), by = "Choice") %>%
  mutate(Prescriptions = replace_na(Prescriptions, 0)) %>%
  mutate(`Department name` = "Hospital-Wide") %>%
  group_by(`Department name`) %>%
  mutate(
    Total = sum(Prescriptions),
    Proportion = ifelse(Total > 0, Prescriptions / Total, 0)
  ) %>%
  ungroup()

# Combine department + hospital data
choice_summary <- bind_rows(choice_summary, hospital_summary)

# Format labels: highlight Hospital-Wide and control order
choice_summary <- choice_summary %>%
  mutate(
    PlotLabel = ifelse(
      `Department name` == "Hospital-Wide",
      "<b style='color:#0072B2;'>Hospital-Wide</b>",
      `Department name`
    ),
    PlotLabel = factor(
      PlotLabel,
      levels = rev(c(
        "<b style='color:#0072B2;'>Hospital-Wide</b>",
        sort(setdiff(unique(`Department name`), "Hospital-Wide"))
      ))
    ),
    Choice = factor(Choice, levels = choice_levels_stack)
  )

# Build the plot
ggplot(choice_summary, aes(x = PlotLabel, y = Proportion, fill = Choice)) +
  
  # Highlight Hospital-Wide row
  annotate("rect", xmin = 0.5, xmax = 1.5, ymin = 0, ymax = 1,
           fill = "gray95", alpha = 0.5) +
  
  # Stacked proportional bars
  geom_bar(stat = "identity", position = "fill", width = 0.85) +
  
  # % labels inside segments (only if >5%)
  geom_text(
    aes(label = ifelse(Proportion > 0.05, scales::percent(Proportion, accuracy = 1), "")),
    position = position_fill(vjust = 0.5),
    size = 3.5, color = "black"
  ) +
  
  # Total n= labels above bars
  geom_text(
    data = choice_summary %>% distinct(PlotLabel, Total),
    aes(x = PlotLabel, y = 1.015, label = paste0("n=", Total)),
    inherit.aes = FALSE,
    size = 3, color = "gray30", hjust = 0
  ) +
  
  # Color scheme and legend (force all to show)
  scale_fill_manual(
    breaks = choice_levels_legend,
    values = c(
      "First choice"  = "#8E44AD",
      "Second choice" = "#00BCD4"
    ),
    drop = FALSE
  ) +
  
  # Flip to horizontal bars
  coord_flip(ylim = c(0, 1.04)) +
  
  # Labels and titles
  labs(
    title = "Use of Recommended IV Antibiotics by Line of Treatment",
    subtitle = "Proportions by department (percentages shown inside bars)",
    x = "Department",
    y = "Proportion of Patients",
    fill = "Treatment Choice"
  ) +
  
  # Theme and styling
  theme_minimal(base_size = 10) +
  theme(
    axis.text.y = ggtext::element_markdown(size = 9),  # bold Hospital-Wide
    axis.text.x = element_text(size = 9),
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    panel.border = element_rect(color = "gray70", fill = NA),
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    plot.margin = margin(10, 10, 10, 10)
  )



```

---

<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📝 Summary of Antibiotic Choice Appropriateness for BJIs
</h2>

This section summarises the proportion of antibiotic **choice appropriateness** for BJIs across hospital departments based on the WHO AWaRe Book.


```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}
# Exclude hospital-wide row for department-level counts 
qi_summary_BJ_filtered <- qi_summary_BJ %>%
  filter(`Department name` != "Hospital-Wide")

# Total eligible patients (excluding "Not eligible") 
total_eligible <- qi_summary_BJ_filtered %>%
  filter(!Indicator %in% c("Not eligible for AWaRe BJI QIs")) %>%
  summarise(Total = sum(Patients, na.rm = TRUE)) %>%
  pull(Total)

# Total who received IV antibiotics 
total_iv <- qi_summary_BJ_filtered %>%
  filter(Indicator %in% c(
    "Received recommended IV antibiotics", 
    "Partially received recommended IV antibiotics", 
    "Received IV antibiotics not among recommended options"
  )) %>%
  summarise(Total = sum(Patients, na.rm = TRUE)) %>%
  pull(Total)

#  HANDLE IF NO IV PATIENTS 
if (total_iv == 0) {
  final_summary_html <- HTML(glue::glue(
    "<div style='background-color: #fff3cd; border-left: 5px solid #ffc107; padding: 14px;'>
    ⚠️ <strong>No summary available</strong> — there are currently no eligible BJI patients who received IV antibiotics.<br><br>
    <em>This may indicate no patients met inclusion criteria or received IV antibiotics during the reporting period.</em>
    </div>"
  ))
  htmltools::browsable(final_summary_html)

} else {

  # Summarise proportions per department (excluding Hospital-Wide) 
  summary_data_BJ <- qi_summary_BJ_filtered %>%
    filter(Indicator %in% c(
      "Received recommended IV antibiotics", 
      "Partially received recommended IV antibiotics", 
      "Received IV antibiotics not among recommended options"
    )) %>%
    group_by(`Department name`, Indicator) %>%
    summarise(Patients = sum(Patients), .groups = "drop") %>%
    pivot_wider(names_from = Indicator, values_from = Patients, values_fill = 0) %>%
    mutate(
      Total = `Received recommended IV antibiotics` +
              `Partially received recommended IV antibiotics` +
              `Received IV antibiotics not among recommended options`,
      Prop_Full = `Received recommended IV antibiotics` / Total,
      Prop_Partial = `Partially received recommended IV antibiotics` / Total,
      Prop_None = `Received IV antibiotics not among recommended options` / Total
    ) %>%
    filter(Total > 0)

  # Add Hospital-Wide row separately (aggregate only for display) 
  hospital_row <- summary_data_BJ %>%
    summarise(
      `Department name` = "Hospital-Wide",
      `Received recommended IV antibiotics` = sum(`Received recommended IV antibiotics`),
      `Partially received recommended IV antibiotics` = sum(`Partially received recommended IV antibiotics`),
      `Received IV antibiotics not among recommended options` = sum(`Received IV antibiotics not among recommended options`)
    ) %>%
    mutate(
      Total = `Received recommended IV antibiotics` +
              `Partially received recommended IV antibiotics` +
              `Received IV antibiotics not among recommended options`,
      Prop_Full = `Received recommended IV antibiotics` / Total,
      Prop_Partial = `Partially received recommended IV antibiotics` / Total,
      Prop_None = `Received IV antibiotics not among recommended options` / Total
    )

  # Combine Hospital-Wide + department summaries 
  summary_data_combined <- bind_rows(hospital_row, summary_data_BJ)

  # Intro block 
  intro_text <- glue::glue(
    "   <div style='background-color: #f8f9fa; border-left: 5px solid #17a2b8; padding: 14px; margin-top: 10px; margin-bottom: 10px;'>
    💊 <strong>Denominator:</strong> Number of eligible patients who received any IV antibiotics for BJIs (<strong>{total_iv}</strong> out of {total_eligible}).
    </div><br><br>
    <strong>Summary:</strong><br><br>"
  )

  # Format <ul> blocks for each department 
  formatted_blocks <- summary_data_combined %>%
    mutate(block = pmap_chr(
      list(
        `Department name`,
        Prop_Full, `Received recommended IV antibiotics`,
        Prop_Partial, `Partially received recommended IV antibiotics`,
        Prop_None, `Received IV antibiotics not among recommended options`,
        Total
      ),
      function(dept, full_p, full_n, part_p, part_n, none_p, none_n, total_n) {
        color <- if (dept == "Hospital-Wide") "#0072B2" else "#6c757d"
        bg <- if (dept == "Hospital-Wide") "#f0f0f0" else "#ffffff"

        glue::glue(
          "<div style='background-color: {bg}; border-left: 5px solid {color}; padding: 14px; margin-bottom: 20px;'>
          <strong>🏥 {dept}</strong> <span style='color: #888;'>(n = {total_n} patients)</span><br><br>
          <ul style='margin-left: 1.2em; line-height: 1.7; padding-left: 0; list-style-type: none;'>
            <li>✅ <strong>Received recommended IV antibiotics</strong> (as per WHO AWaRe Book): <strong>{scales::percent(full_p, accuracy = 0.1)}</strong> ({full_n} out of {total_n})</li>
            <li>⚠️ <strong>Partially received recommended IV antibiotics</strong> (as per WHO AWaRe Book): <strong>{scales::percent(part_p, accuracy = 0.1)}</strong> ({part_n} out of {total_n})</li>
            <li>❌ <strong>Received IV antibiotics not among recommended options</strong> (as per WHO AWaRe Book): <strong>{scales::percent(none_p, accuracy = 0.1)}</strong> ({none_n} out of {total_n})</li>
          </ul>
          </div>"
        )
      }
    ))

  # Combine and render output 
  final_summary_html <- HTML(paste0(intro_text, paste(formatted_blocks$block, collapse = "\n")))
  htmltools::browsable(final_summary_html)
}

```



---

<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📈 Antibiotic Choice & Dosage Appropriateness for BJIs
</h2>

```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}


# Data preparation: antibiotic choice & dosage appropriateness

#   Filter BJ Patients and Add AWaRe Eligibility 
data_BJ2 <- data_patients %>%
  filter(`Diagnosis code` == "BJ") %>%
  mutate(
    Route = toupper(Route),
    ATC5 = trimws(toupper(ATC5)),
    AWaRe_compatible = ifelse(
      `Age years` >= 18 & Indication == "CAI" & Treatment == "EMPIRICAL" & AWaRe %in% AWaRe_abx, TRUE, FALSE
    )
  )

#   Lookup Drug & Dose Info 
lookup2 <- data_lookup %>% filter(Code == "H_OAI_APPROP_DOSAGE")
lookup_names2 <- unlist(lookup2[1, c("ABX-ATC-1", "ABX-ATC-2", "ABX-ATC-3", "ABX-ATC-4", "ABX-ATC-5", "ABX-ATC-6")], use.names = FALSE)
lookup_names2 <- toupper(trimws(lookup_names2))

#   Compute Total Daily Dose for each row  
data_BJ2 <- data_BJ2 %>%
  mutate(
    Unit_Factor = case_when(
      Unit == "mg" ~ 1,
      Unit == "g"  ~ 1000,
      TRUE         ~ NA_real_
    ),
    Total_Daily_Dose = as.numeric(`Single Unit Dose`) * as.numeric(`N Doses/day`) * Unit_Factor
  )

#   Match Drug + Dose + Route 
for (i in 1:6) {
  name_col <- paste0("ABX-ATC-", i)
  dose_col <- paste0("ABX-DOSE-", i)
  freq_col <- paste0("ABX-DAY-DOSE-", i)
  unit_col <- paste0("ABX-UNIT-", i)
  route_col <- paste0("ABX-ROUTE-", i)

  dose_match_col <- paste0("Match_Drug_Dose_", i)

  # Standardise lookup info
  expected_dose <- as.numeric(lookup2[[dose_col]]) * as.numeric(lookup2[[freq_col]])
  dose_unit_factor <- case_when(
    lookup2[[unit_col]] == "mg" ~ 1,
    lookup2[[unit_col]] == "g"  ~ 1000,
    TRUE                       ~ NA_real_
  )
  total_expected_dose <- expected_dose * dose_unit_factor
  drug_lookup <- toupper(trimws(lookup2[[name_col]]))

  # Create matching column
  data_BJ2[[dose_match_col]] <- ifelse(
    data_BJ2$ATC5 == drug_lookup &
      abs(data_BJ2$Total_Daily_Dose - total_expected_dose) < 1,
    TRUE, FALSE
  )
}  

#   Summarise at Patient Level 
patient_summary2 <- data_BJ2 %>%
  filter(AWaRe_compatible) %>%
  group_by(`Survey Number`, `Department name`) %>%
  summarise(
    Match_1_P = any(ATC5 == lookup_names2[1] & Route == "P"),
    Match_2_P = any(ATC5 == lookup_names2[2] & Route == "P"),
    Match_3_P = any(ATC5 == lookup_names2[3] & Route == "P"),
    Match_4_P = any(ATC5 == lookup_names2[4] & Route == "P"),
    Match_5_P = any(ATC5 == lookup_names2[5] & Route == "P"),
    Match_6_P = any(ATC5 == lookup_names2[6] & Route == "P"),

    Dose_1_OK = any(Match_Drug_Dose_1),
    Dose_2_OK = any(Match_Drug_Dose_2),
    Dose_3_OK = any(Match_Drug_Dose_3),
    Dose_4_OK = any(Match_Drug_Dose_4),
    Dose_5_OK = any(Match_Drug_Dose_5),
    Dose_6_OK = any(Match_Drug_Dose_6),

    Any_IV = any(Route == "P"),
    .groups = "drop"
  ) %>%
  mutate(
    Any_Match = Match_1_P | Match_2_P | Match_3_P | Match_4_P | Match_5_P | Match_6_P,
    Any_Correct_Dose = 
      (Match_1_P & Dose_1_OK) |
      (Match_2_P & Dose_2_OK) |
      (Match_3_P & Dose_3_OK) |
      (Match_4_P & Dose_4_OK) |
      (Match_5_P & Dose_5_OK) |
      (Match_6_P & Dose_6_OK),

    Dose_Result = case_when(
      Any_Correct_Dose ~ "Received recommended IV antibiotic with recommended dosage",
      Any_Match & !Any_Correct_Dose ~ "Received recommended IV antibiotic without recommended dosage",
      Any_IV & !Any_Match ~ "Received IV antibiotics not among recommended options",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(Dose_Result))


# Summarise by department 
iv_dose_counts <- patient_summary2 %>%
  count(`Department name`, Dose_Result, name = "Patients")

# Complete combinations: all depts × both results
all_combos2 <- expand_grid(
  `Department name` = unique(patient_summary2$`Department name`),
  Dose_Result = c("Received recommended IV antibiotic with recommended dosage", "Received recommended IV antibiotic without recommended dosage", "Received IV antibiotics not among recommended options")
)

# Merge and fill missing
iv_dose_summary2 <- all_combos2 %>%
  left_join(iv_dose_counts, by = c("Department name", "Dose_Result")) %>%
  mutate(Patients = replace_na(Patients, 0)) %>%
  group_by(`Department name`) %>%
  mutate(Total = sum(Patients),
         Proportion = round(100 * Patients / Total, 1)) %>%
  ungroup()

#  Hospital-Wide row
hospital_row2 <- iv_dose_summary2 %>%
  group_by(Dose_Result) %>%
  summarise(Patients = sum(Patients), .groups = "drop") %>%
  mutate(`Department name` = "Hospital-Wide") %>%
  group_by(`Department name`) %>%
  mutate(Total = sum(Patients),
         Proportion = round(100 * Patients / Total, 1)) %>%
  ungroup()

#  Final summary table
final_summary2 <- bind_rows(iv_dose_summary2, hospital_row2) %>%
  arrange(`Department name`, Dose_Result)

```


This visual summarises the proportion of antibiotic choice & dosage appropriateness for IAIs across hospital departments based on the WHO AWaRe Book.
 
```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}
# Order factor for bar stacking
final_summary2$Dose_Result <- factor(
  final_summary2$Dose_Result,
  levels = c("Received recommended IV antibiotic with recommended dosage", "Received recommended IV antibiotic without recommended dosage", "Received IV antibiotics not among recommended options")
)

#  Create styled PlotLabel
final_summary2 <- final_summary2 %>%
  mutate(
    PlotLabel = ifelse(
      `Department name` == "Hospital-Wide",
      "<b style='color:#0072B2;'>Hospital-Wide</b>",
      `Department name`
    )
  )

# Define factor order (Hospital-Wide first, rest sorted)
ordered_labels <- c(
  "<b style='color:#0072B2;'>Hospital-Wide</b>",
  sort(unique(final_summary2$PlotLabel[final_summary2$PlotLabel != "<b style='color:#0072B2;'>Hospital-Wide</b>"]))
)
final_summary2$PlotLabel <- factor(final_summary2$PlotLabel, levels = rev(ordered_labels))

#  Extract unique n= label data with PlotLabel applied
label_data <- final_summary2 %>%
  distinct(`Department name`, Total) %>%
  mutate(
    PlotLabel = ifelse(
      `Department name` == "Hospital-Wide",
      "<b style='color:#0072B2;'>Hospital-Wide</b>",
      `Department name`
    ),
    PlotLabel = factor(PlotLabel, levels = levels(final_summary2$PlotLabel))
  )

#  Plot
ggplot(final_summary2, aes(x = PlotLabel, y = Proportion, fill = Dose_Result)) +

  # Highlight hospital-wide row
  annotate("rect",
           xmin = 0.5, xmax = 1.5, ymin = 0, ymax = 1,
           fill = "gray95", alpha = 0.5) +

  # Stacked bars
  geom_bar(stat = "identity", position = "fill", width = 0.85) +

  # Count % inside bars
  geom_text(
    aes(label = ifelse(Proportion > 0.05, paste0(round(Proportion * 1, 1), "%"), "")),
    position = position_fill(vjust = 0.5),
    size = 3, color = "black"
  ) +

  # n= labels on top
  geom_text(
    data = label_data,
    aes(x = PlotLabel, y = 1.015, label = paste0("n=", Total)),
    inherit.aes = FALSE,
    size = 3, color = "gray30", hjust = 0
  ) +

  # Custom fill colors
  scale_fill_manual(
    breaks = c("Received recommended IV antibiotic with recommended dosage", "Received recommended IV antibiotic without recommended dosage", "Received IV antibiotics not among recommended options"),
    values = c("Received recommended IV antibiotic with recommended dosage" = "#084594", "Received recommended IV antibiotic without recommended dosage" = "#FC9272", "Received IV antibiotics not among recommended options" = "#D3D3D3")
  ) +

  coord_flip(ylim = c(0, 1.05)) +

  labs(
    title = "Summary of Dosage Appropriateness for BJIs Cases with Recommended Antibiotic Choices",
    subtitle = "Each bar shows distribution of appropriateness against WHO AWaRe guidelines (n = raw patient counts)",
    x = "Department",
    y = "Proportional Stacked Bars",
    fill = "Treatment Appropriateness Category"
  ) +

  theme_minimal(base_size = 12) +
  theme(
    axis.text.y = element_markdown(size = 8),  
    axis.title = element_text(face = "bold"),
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    legend.text = element_text(margin = margin(r = 2)),
    plot.title = element_text(face = "bold", hjust = 0.5, size = 10),
    plot.subtitle = element_text(hjust = 0.5, size = 8, color = "gray30"),
    panel.border = element_rect(color = "gray70", fill = NA, size = 0.8),
    plot.margin = margin(10, 80, 10, 10)
  ) +
  guides(
    fill = guide_legend(nrow = 3, byrow = TRUE, title.position = "top")
  )



```


<h2 style="color: #4a4a4a; font-weight: bold; margin-top: 1.5em;">
📝 Summary of Antibiotic Dosage Appropriateness for BJI
</h2>

This section summarises the proportion of antibiotic **dosage appropriateness** for BJIs across hospital departments based on the WHO AWaRe Book.

```{r echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE, error=FALSE}
# Exclude Hospital for total count summary 
final_summary2_BJ_filtered <- final_summary2 %>%
  filter(`Department name` != "Hospital-Wide")

#  Calculate total eligible patients who received IV antibiotics with dosage data 
total_approp_iv_given <- final_summary2_BJ_filtered %>%
  filter(Dose_Result %in% c("Received recommended IV antibiotic with recommended dosage", "Received recommended IV antibiotic without recommended dosage")) %>%
  summarise(Total = sum(Patients, na.rm = TRUE)) %>%
  pull(Total)

#  HANDLE EMPTY CASE 
if (total_approp_iv_given == 0) {

  final_summary_html2 <- HTML(glue::glue(
    "<div style='background-color: #fff3cd; border-left: 5px solid #ffc107; padding: 14px; margin-top: 10px;'>
    ⚠️ <strong>No summary available</strong> — there are currently no BJI patients who received a recommended IV antibiotic with dosage data.<br><br>
    <em>This may indicate that no patients received antibiotics with recommended dosing, or none met inclusion criteria.</em>
    </div>"
  ))

  htmltools::browsable(final_summary_html2)

} else {

  # Indicator intro explanation 
  intro_text2 <- glue::glue(
    "<div style='background-color: #f8f9fa; border-left: 5px solid #17a2b8; padding: 14px; margin-top: 10px; margin-bottom: 10px;'>
    💊 <strong>Denominator:</strong> Number of eligible BJI patients who received any recommended (<em>or partially recommended</em>) IV antibiotic choice based on WHO AWaRe Book (<strong>{total_approp_iv_given}</strong> out of <strong>{total_eligible}</strong>).
    </div><br><br>
    <strong>Summary:</strong><br><br>"
  )

  # Ensure complete combinations (in case of missing dose categories) 
  dept_list <- unique(final_summary2$`Department name`)
  dose_categories <- c(
    "Received recommended IV antibiotic with recommended dosage",
    "Received recommended IV antibiotic without recommended dosage"
  )

  complete_summary <- expand_grid(
    `Department name` = dept_list,
    Dose_Result = dose_categories
  ) %>%
    left_join(final_summary2, by = c("Department name", "Dose_Result")) %>%
    mutate(
      Patients = replace_na(Patients, 0),
      Total = ave(Patients, `Department name`, FUN = sum),
      Proportion = ifelse(Total == 0, 0, Patients / Total)
    )

  # Format styled HTML blocks for each department 
  formatted_blocks2 <- complete_summary %>%
    group_by(`Department name`) %>%
    summarise(
      block = {
        dept <- first(`Department name`)
        color <- if (dept == "Hospital-Wide") "#0072B2" else "#6c757d"
        bg <- if (dept == "Hospital-Wide") "#f0f0f0" else "#ffffff"

        glue::glue(
          "<div style='background-color: {bg}; border-left: 5px solid {color}; padding: 14px; margin-bottom: 20px;'>
          <strong>🏥 {dept}</strong> <span style='color: #888;'>(n = {first(Total)} patients)</span><br><br>
          <ul style='margin-left: 1.2em; line-height: 1.7; padding-left: 0; list-style-type: none;'>
            <li>✅ <strong>Received recommended IV antibiotic with recommended dosage</strong> (as per WHO AWaRe Book): <strong>{scales::percent(Proportion[Dose_Result == 'Received recommended IV antibiotic with recommended dosage'], accuracy = 0.1)}</strong> ({Patients[Dose_Result == 'Received recommended IV antibiotic with recommended dosage']} out of {first(Total)})</li>
            <li>❌ <strong>Received recommended IV antibiotic without recommended dosage</strong> (as per WHO AWaRe Book): <strong>{scales::percent(Proportion[Dose_Result == 'Received recommended IV antibiotic without recommended dosage'], accuracy = 0.1)}</strong> ({Patients[Dose_Result == 'Received recommended IV antibiotic without recommended dosage']} out of {first(Total)})</li>
          </ul>
          </div>"
        )
      },
      .groups = "drop"
    )

  # Reorder Hospital-Wide first
  formatted_blocks2 <- formatted_blocks2 %>%
    mutate(order = ifelse(`Department name` == "Hospital-Wide", 0, 1)) %>%
    arrange(order, `Department name`) %>%
    select(-order)

  # Final HTML output
  final_summary_html2 <- HTML(paste0(intro_text2, paste(formatted_blocks2$block, collapse = "\n")))
  htmltools::browsable(final_summary_html2)
}


```